\documentclass[11pt]{article}
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs,array}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\hypersetup{
  pdftitle={The Riemann Kernel Is Globally PF4},
  pdfauthor={Joshuah Rainstar},
  pdfsubject={Strict global PF4 classification of the Riemann kernel},
  pdfkeywords={Polya-frequency function, total positivity, Riemann kernel, entire function, Wronskian, Fourier transform, exact certificate}
}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\R}{\mathbb{R}}
\newcommand{\T}{\mathcal{T}}
\newcommand{\Cfour}{\mathcal{C}_4}
\newcommand{\E}{\mathbb{E}}
\newcommand{\dd}{\,\mathrm{d}}
\newcommand{\PF}{\mathrm{PF}}
\newcommand{\TP}{\mathrm{TP}}
\newcommand{\TN}{\mathrm{TN}}
\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\appref}[1]{Appendix~\ref{#1}}

\numberwithin{equation}{section}

\title{The Riemann Kernel Is Globally \texorpdfstring{$\PF_4$}{PF4}}
\author{Joshuah Rainstar\thanks{Email:
\href{mailto:joshuah.rainstar@gmail.com}{\texttt{joshuah.rainstar@gmail.com}}}}
\date{16 July 2026}

\begin{document}
\maketitle
\begin{abstract}
Let \(\Phi\) be the classical Riemann, or de Bruijn--Newman, kernel. We prove
that its exact global P\'olya-frequency order is four: every translation minor
of order at most four is strictly positive at strictly ordered nodes, whereas
the order-five minor at the exact spacing \(211/2000\) is negative. Both
halves of this classification are exported by a maintained Lean 4 theorem;
the proof depends only on the standard Lean/mathlib axioms. The optional
order-five confluent coefficient changes sign exactly once on the positive
half-line, at \(0.0622795266356<u_*<0.0622795266357\). For the positive half,
a two-mode
argument proves global positivity of the log-curvature quantities \(q,F_2\)
and of the fully confluent invariant \(\Cfour\). The finite verification uses
only rational polynomial algebra, Taylor inequalities, and geometric tails.
The direct finite-witness certificate likewise uses exact rational arithmetic.
A
quotient-Wronskian argument reduces arbitrary fourth-order minors to
\(\partial_\xi\Psi<0\). In the increasing curvature coordinate, its numerator
is
\[
 \delta\Lambda\int_p^w
 \Delta(t)\frac{\Cfour(t)}{Q(t)^6\kappa(t)^2}\dd t.
\]
Here \(\Delta\) is a deterministic closed cumulative gap built from two
explicitly normalized, curvature-tilted triangular weights. Its strict
positivity follows on the actual coordinate interval from the exact mass
identities and one explicit algebraic sign change; no probability or CDF
premise is required. The transport
reductions and analytic sign estimates are given explicitly, with a table of
the finite polynomial inequalities used for the three global signs.
We then construct an explicit positive even Schwartz kernel which is itself
strictly \(\PF_4\) but whose entire Fourier transform has nonreal zeros; the
latter conclusion follows from a short exact discriminant inequality. This
delimits the finite-order reach of Schoenberg's infinite-order transform
correspondence.
\end{abstract}
\noindent\textbf{2020 Mathematics Subject Classification.}
15B48 (primary); 42A38, 30D15, 11M26 (secondary).

\noindent\textbf{Keywords.}
P\'olya-frequency function, total positivity, Riemann kernel, entire function,
Wronskian, Fourier transform, exact certificate.
\tableofcontents

\section{Introduction}\label{sec:introduction}

A function \(f:\R\to\R\) is \(\PF_r\) when every translation-kernel minor
\[
 \det[f(x_i-y_j)]_{i,j=1}^k
\]
is nonnegative for \(1\leq k\leq r\) and increasing node tuples. We call the
property strict when the determinant is positive whenever both tuples are
strictly increasing. This paper determines the exact finite P\'olya-frequency
order of the Riemann kernel; see \cite{belton} for modern background and
Schoenberg's characterization. Related finite-order and Riemann-kernel work is
placed in \secref{sec:related-work}.

\begin{theorem}[Exact global PF order]\label{thm:main}
The exact global P\'olya-frequency order of \(\Phi\) is four. More precisely:
\begin{enumerate}
\item for every \(1\leq k\leq4\) and strictly increasing real tuples
\(x_1<\cdots<x_k\) and \(y_1<\cdots<y_k\),
\[
 \det[\Phi(x_i-y_j)]_{i,j=1}^k>0.
\]
\item with \(h=211/2000\),
\[
 \det[\Phi((i-j)h)]_{i,j=0}^4<0.
\]
\end{enumerate}
\end{theorem}

The two theorem inputs are deliberately separated. The positive input is the
universal strict-order theorem through four. The negative input is the direct
rational order-five witness in part~(2), including proved strict ordering of
its nodes and the signed Toeplitz-to-translation-matrix identification. In the
maintained formal development these are assembled by
\path{PF4.globalRiemannKernel_pfOrderExactly_four}; its axiom audit reports
only \texttt{propext}, \texttt{Classical.choice}, and \texttt{Quot.sound}.

The exact-order classification and the Fourier question are distinct. The
following example marks a precise finite-order boundary for Schoenberg's
infinite-order transform correspondence, even within the positive even
Schwartz class.

\begin{theorem}[Continuous \(\PF_4\) Fourier separator]\label{thm:separator}
There is an explicit positive even Schwartz function \(f_*\) which is strict
\(\PF_4\), while its entire Fourier transform has nonreal zeros.
Consequently continuous \(\PF_3\) and continuous \(\PF_4\) membership are
each insufficient to force Fourier real-rootedness.
\end{theorem}

The proof has two one-variable inputs and one exact transport
mechanism. First, global inequalities \(q>0\) and \(F_2>0\) imply strict
\(\PF_3\) and positivity of a three-point functional \(\Lambda\). Second, the
fully confluent order-four invariant \(\Cfour\) is globally positive. Exact
quotient identities reduce strict \(\PF_4\) to the monotonicity of a scalar
three-point function \(\Psi\). On the actual image of an increasing curvature
coordinate, the derivative of \(\Psi\) becomes a positive integral of
\(\Cfour\) against a deterministic closed cumulative gap.

The finite part of the positive input consists of exact rational Bernstein
coefficients on fixed algebraic domains, followed by analytic bounds for all
remaining theta modes; \appref{app:tail} lists the transformed target
polynomials, domains, degrees, minimum coefficients, derivative envelopes,
and the surviving relative margins. The transport algebra is proved in the
text, and the order-five
calculation uses rational enclosures and elementary series bounds.
An optional recurrence gives a global order-five refinement: its confluent
coefficient has one positive zero, enclosed in a rational interval of width
\(10^{-13}\), and an explicit rational spacing gives a comfortably negative
finite determinant. Neither refinement is needed for the strict-\(\PF_4\)
theorem; it records additional structure around the direct witness.
Theorem~\ref{thm:separator}, proved in \secref{sec:separator}, supplies an
explicit order-four counterexample rather than a finite-order sufficiency
threshold.
\section{Relation to earlier work}\label{sec:related-work}

Schoenberg introduced P\'olya-frequency functions and connected translation
minors with bilateral Laplace transforms and variation-diminishing convolution
operators~\cite{schoenberg-ii,belton}. Karlin's monograph remains the
standard systematic account of total positivity and its composition
principles~\cite{karlin}; a modern review of PF functions and their preservers
is given by Belton, Guillot, Khare, and Putinar~\cite{belton}.

Finite-order translation kernels have a substantially wider range than the
infinite-order class. Khare's characterization of measurable \(\TN_p\)
functions for \(p\geq3\) provides a general finite-order setting~\cite{khare}.
The present proof instead derives a criterion specific to order four, using
successive quotient derivatives and a curvature transport identity.

The theta normalization used here is the classical one in de Bruijn's study of
the Riemann Fourier kernel~\cite{debruijn}. For the same kernel, Dimitrov and Xu
relate Wronskians of Fourier and Laplace transforms to correlation kernels and
real-zero criteria~\cite{dimitrov-xu}, while Csordas and Varga obtain strict
concavity and moment inequalities connected with the Riemann
Hypothesis~\cite{csordas-varga}. Grochenig explains the distinct Schoenberg
correspondence relevant to the Riemann Hypothesis: the PF function there is
recovered from the reciprocal of a Laguerre--P\'olya entire function, rather than
identified with the original Riemann kernel~\cite{grochenig}.

Micha\l{}owski first published an explicit negative \(5\times5\) Toeplitz
minor for this kernel, supported by an interval computation, together with
single-configuration positivity checks at orders at most
four~\cite{michalowski}. Global \(\PF_4\) and a symbolic proof of the order-five
leading sign are posed there as Open Problems 1 and 2. Theorem~\ref{thm:main}
resolves the first, and Lemma~\ref{lem:origin-pf5-sign} resolves the second in
strengthened form. Indeed, for the Toeplitz determinant
\[
 D_r(u_0,h)=\det[\Phi(u_0+(i-j)h)]_{i,j=0}^{r-1},
\]
Lemma~\ref{lem:confluent-limit} gives its leading coefficient as
\[
 C_r(u_0)=
 \frac{(-1)^{r(r-1)/2}V(0,\ldots,r-1)^2}
 {\prod_{k=0}^{r-1}(k!)^2}
 \det[\Phi^{(i+j)}(u_0)]_{i,j=0}^{r-1}.
\]
For \(r=5\) the sign factor is positive, only derivatives through order eight
occur, and the limit as \(u_0\to0^+\) is a positive multiple of the
parity-factorized determinant \(\mathsf H_5=CB<0\) computed exactly in
Lemma~\ref{lem:origin-pf5-sign}. Theorem~\ref{thm:confluent-threshold}
determines the complete sign change: \(C_5(u_0)<0\) precisely for
\(0\leq u_0<u_*\), where
\(0.0622795266356<u_*<0.0622795266357\). The normalization in
\cite{michalowski} uses \(K_M(u)=\Phi(2u)/2\), so its corresponding center is
\(u_*/2\in(0.0311397633178,0.03113976331785)\).

Theorem~\ref{thm:separator} further shows where the infinite-order transform
conclusion ceases to follow from finite-order positivity: even strict
\(\PF_3\) or \(\PF_4\) does not control all Fourier zeros.
\section{The kernel and smooth even continuation}\label{sec:kernel}

Put
\[
 \vartheta(x)=\sum_{n\in\mathbb Z}e^{-\pi n^2x},\qquad
 \Theta(t)=\vartheta(e^{2t}),\qquad H(t)=e^{t/2}\Theta(t).
\]
This is a real-valued definition: summability is first proved directly for
every \(x>0\), before any analytic continuation is invoked. The real
specialization of Gaussian Poisson summation gives the exact normalization
\(\vartheta(x)=x^{-1/2}\vartheta(1/x)\), and hence
\[
 \Theta(-t)=e^t\Theta(t),\qquad H(-t)=H(t).
\]
A Jacobi-theta realization supplies a globally analytic function agreeing
with this real series. Thus \(H\) is real analytic and even. Define
\[
 \Phi(t)=\frac12\left(H''(t)-\frac14H(t)\right).
\]
This is twice the common de Bruijn kernel normalization; multiplication by a
positive constant changes none of the PF signs or strictness statements.
On \(t\geq0\), locally uniform polynomial--geometric majorants justify
termwise differentiation through order six and give
\begin{equation}\label{eq:kernel-series}
 \Phi(t)=\sum_{n\geq1}
 \left(4\pi^2n^4e^{9t/2}-6\pi n^2e^{5t/2}\right)
 e^{-\pi n^2e^{2t}}.
\end{equation}
Parity reflects this identity to every real \(t\), equivalently by replacing
\(t\) on the right by \(|t|\). Thus the positive-side formula is the
restriction of a real-analytic even function. Smoothness and every derivative
used later at the origin are consequences of that analytic realization, not
of numerical coverage or of differentiating an absolute-value definition.

For \(t\geq0\), the coefficient of the \(n\)-th exponential can be factored as
\[
 2\pi n^2e^{5t/2}\bigl(2\pi n^2e^{2t}-3\bigr)>0,
\]
because \(2\pi>3\). Hence every term in \eqref{eq:kernel-series} is positive
and \(\Phi(t)>0\) on \([0,\infty)\). Evenness gives \(\Phi(t)>0\) on all of
\(\R\), so the following logarithm is globally defined.

Write
\[
 \ell=\log\Phi,\qquad s=\ell',\qquad q=-s'=-\ell''.
\]
For \(a<b\), define
\begin{equation}\label{eq:AM}
 A(a,b)=s(a)-s(b),\qquad
 M(a,b)=\frac{q(b)-q(a)}{A(a,b)}.
\end{equation}
When \(q>0\), \(s\) is strictly decreasing and \(A(a,b)>0\).

\begin{sloppypar}
The maintained formal boundary mirrors this order of construction.
\path{PF4.riemannTheta_modular} is the library-backed Poisson step;
\path{PF4.contDiff_riemannH},
\path{PF4.globalRiemannKernel_even}, and
\path{PF4.globalRiemannKernel_eq_thetaSeries_abs} give analytic continuation,
parity, and the reflected series; and
\path{PF4.GlobalKernelJetIdentification.iteratedDeriv_globalRiemannKernel_eq_thetaSeriesJet}
identifies the complete jet through order six. No project-specific axiom is
used by these declarations.
\end{sloppypar}
\section{Certified one-variable inputs}\label{sec:inputs}

Define
\[
 F_1=qq''-(q')^2,\qquad F_2=q^3-F_1.
\]
For the logarithmic cumulants \(c_j=\ell^{(j)}\), set
\[
\begin{aligned}
 &m_0=1,\quad m_1=0,\quad m_2=c_2,\quad m_3=c_3,\\
 &m_4=c_4+3c_2^2,\quad m_5=c_5+10c_2c_3,\\
 &m_6=c_6+15c_2c_4+10c_3^2+15c_2^3,
\end{aligned}
\]
and
\begin{equation}\label{eq:C4-def}
 \Cfour(t)=\det[m_{i+j-2}(t)]_{i,j=1}^4.
\end{equation}

\begin{lemma}[Certified input]\label{lem:certified-input}
For the kernel \(\Phi\),
\[
 q(t)>0,\qquad F_2(t)>0,\qquad \Cfour(t)>0
 \quad(t\in\R).
\]
\end{lemma}

The proof combines exact rational polynomial inequalities with analytic
theta-tail bounds. For \(u\geq0\), put
\[
 x=\pi e^{2u},\qquad \eta=e^{-3x},\qquad R_0(z)=2z-3,
\]
and recursively
\[
 R_{j+1}(z)=\left(\frac52-2z\right)R_j(z)+2zR_j'(z).
\]
After division by the positive first theta mode, the first two modes give the
normalized jet entries
\[
 a_j(x,\eta)=\frac{R_j(x)+4\eta R_j(4x)}{R_0(x)}.
\]
Exact rational Bernstein coefficients on three fixed algebraic domains prove
\[
 q_{1,2}>10,\qquad (F_2)_{1,2}>1000,
 \qquad (\Cfour)_{1,2}>50{,}000{,}000.
\]
Here the half-line certificates are applied directly to the cleared
numerators of the shifted targets \(q_{1,2}-10\),
\((F_2)_{1,2}-1000\), and
\((\Cfour)_{1,2}-50{,}000{,}000\). The complete contribution of modes
\(n\geq3\) is bounded by one monotone polynomial-geometric estimate. Its
changes in the same cleared sign numerators are smaller than the three
displayed margins, both on
\(\pi\leq x\leq5\) and on \(x\geq5\). Evenness completes the real line.
All inequalities, including the derivative envelopes used on the tail, are
derived in \appref{app:tail}. The exact replay uses no floating
point, no interval subdivision, and no FLINT or Arb arithmetic.

\begin{sloppypar}
In the maintained Lean development the compact and outer regions are one
universal theorem, rather than sampled checks. The declarations
\path{PF4.CERT12OuterClosure.normalized_clearedQ_pos},
\path{PF4.CERT12OuterClosure.normalized_clearedF2_pos}, and
\path{PF4.CERT12OuterClosure.normalized_clearedC4_pos} prove the three cleared
signs for every \(t\geq0\). Exact raw-jet identities then remove the positive
denominators, and the reflected global jet from \secref{sec:kernel} covers the
negative half-line and the origin. The Python verifier remains an independent
exact replay of the printed rational certificate; it is not the trusted bridge
from sampled arithmetic to the universal statement.
\end{sloppypar}
\section{Order three and the positive slope functional}\label{sec:pf3}

For \(\xi<m<r\), define
\begin{equation}\label{eq:Lambda}
 \Lambda(\xi;m,r)=A(\xi,r)+M(\xi,m)-M(m,r).
\end{equation}
We give the full estimate used to prove its positivity.

Set \(f_0=q'/q\). Because \(s'=-q\),
\[
 M(a,b)=\frac{\int_a^bq'(t)\dd t}{\int_a^bq(t)\dd t}
       =\frac{\int_a^b f_0(t)q(t)\dd t}{\int_a^bq(t)\dd t};
\]
thus \(M(a,b)\) is a \(q\)-weighted mean of \(f_0\). Choose a point
\(u\in[\xi,m]\) where \(f_0\) is minimal on the left interval and a point
\(v\in[m,r]\) where it is maximal on the right. The weighted-mean bounds and
the ordering of the extremizers are
\[
 M(\xi,m)\geq f_0(u),\qquad M(m,r)\leq f_0(v),
 \qquad u\leq m\leq v.
\]
Consequently
\[
 M(m,r)-M(\xi,m)\leq f_0(v)-f_0(u)
 \leq\int_\xi^r\max(f_0'(t),0)\dd t.
\]
Since
\[
 f_0'=\frac{qq''-(q')^2}{q^2}=\frac{F_1}{q^2}
\]
and \(A(\xi,r)=\int_\xi^r q(t)\dd t\), equation
\eqref{eq:Lambda} yields
\begin{align}
 \Lambda(\xi;m,r)
 &\geq\int_\xi^r\left(q-\frac{\max(F_1,0)}{q^2}\right)\dd t\\
 &=\int_\xi^r\frac{q^3-\max(F_1,0)}{q^2}\dd t
 =\int_\xi^r\frac{\min(q^3,F_2)}{q^2}\dd t>0.
 \label{eq:Lambda-lower}
\end{align}
The second equality uses
\(q^3-\max(F_1,0)=\min(q^3,q^3-F_1)=\min(q^3,F_2)\); the last inequality
follows from Lemma~\ref{lem:certified-input} and \(q>0\).

The same quantity is the logarithmic slope derivative in the normalized
order-three determinant. Hence \eqref{eq:Lambda-lower}, together with strict
log-concavity, proves strict global \(\PF_3\). We rederive the needed
Wronskian form in the next section, where the quotient integral transfers
these confluent signs to every ordered collocation minor.
\section{Quotient-Wronskian reduction}\label{sec:quotient}

Fix \(y_1<y_2<y_3<y_4\), put \(u_j(t)=\Phi(t-y_j)\), and write
\(p_j=t-y_j\), so \(p_4<p_3<p_2<p_1\). Define
\[
 v_j=(u_j/u_1)',\qquad w_j=(v_j/v_2)'.
\]
These quotients are introduced only after their denominators are known to be
positive: \(u_1>0\) by \secref{sec:kernel}, and \(v_2>0\) by the next
display. Later division by \(w_3\) is likewise made only after
\eqref{eq:gj-Lambda} proves \(w_3>0\).
Strict log-concavity gives
\[
 v_j=\frac{u_j}{u_1}A(p_j,p_1)>0\qquad(j\geq2).
\]
The case \(k=2\) of Lemma~\ref{lem:quotient-integral} below therefore proves
strict order two directly.
At the fixed orders used in this paper, successive column division and
differentiation give the exact three-stage cascade
\begin{align}
 W(u_1,u_2,u_3)&=u_1^3W(v_2,v_3),\label{eq:W3-quotient}\\
 W(u_1,u_2,u_3,u_4)&=u_1^4W(v_2,v_3,v_4),\label{eq:W4-first}\\
 W(v_2,v_3,v_4)&=v_2^3W(w_3,w_4),\label{eq:W4-second}\\
 W(w_3,w_4)&=w_3^2\frac{\dd}{\dd t}
 \left(\frac{w_4}{w_3}\right).\label{eq:W4-third}
\end{align}
Consequently
\begin{equation}\label{eq:W4-quotient}
 W(u_1,u_2,u_3,u_4)=u_1^4v_2^3w_3^2
 \frac{\dd}{\dd t}\left(\frac{w_4}{w_3}\right).
\end{equation}
No sign premise is used in these algebraic identities beyond the stated
nonvanishing needed to form the quotients.

Let \(\T\) denote simultaneous translation of all point arguments. From
\eqref{eq:AM},
\begin{equation}\label{eq:TlogA}
 \T A(a,b)=q(b)-q(a),\qquad \T\log A(a,b)=M(a,b).
\end{equation}
The sign convention in \eqref{eq:TlogA} will be used below. Since
\[
 \frac{v_j}{v_2}=\frac{u_j}{u_2}
 \frac{A(p_j,p_1)}{A(p_2,p_1)},
\]
direct differentiation gives
\begin{equation}\label{eq:gj-expanded}
 g_j:=\T\log(v_j/v_2)
 =A(p_j,p_2)+M(p_j,p_1)-M(p_2,p_1).
\end{equation}
The exact weighted-mean split
\[
 A(p_j,p_1)M(p_j,p_1)
 =A(p_j,p_2)M(p_j,p_2)+A(p_2,p_1)M(p_2,p_1)
\]
turns \eqref{eq:gj-expanded} into
\begin{equation}\label{eq:gj-Lambda}
 g_j=\frac{A(p_j,p_2)}{A(p_j,p_1)}
 \Lambda(p_j;p_2,p_1)>0.
\end{equation}
Thus \(w_j=(v_j/v_2)g_j>0\), and
\eqref{eq:W3-quotient} has the strict order-three sign.

Define
\[
 \Psi(\xi;m,r)=\Lambda(\xi;m,r)+\T\log\Lambda(\xi;m,r).
\]
Because \(w_j=(v_j/v_2)g_j\),
\begin{equation}\label{eq:L4-first}
 \T\log(w_4/w_3)
 =(g_4+\T\log g_4)-(g_3+\T\log g_3).
\end{equation}
Equation \eqref{eq:gj-Lambda} and \eqref{eq:TlogA} give
\[
 \T\log g_j=M(p_j,p_2)-M(p_j,p_1)+\T\log\Lambda_j,
\]
where \(\Lambda_j=\Lambda(p_j;p_2,p_1)\). A second use of the same mean split
gives
\[
 g_j+M(p_j,p_2)-M(p_j,p_1)=\Lambda_j-A(p_2,p_1).
\]
The common last term cancels in \eqref{eq:L4-first}, yielding the exact
identity
\begin{equation}\label{eq:L4-Psi}
 \T\log(w_4/w_3)
 =\Psi(p_4;p_2,p_1)-\Psi(p_3;p_2,p_1).
\end{equation}

\begin{lemma}[Iterated quotient integral]\label{lem:quotient-integral}
Let \(f_1,\ldots,f_k\) be continuously differentiable on an interval,
let \(f_1>0\), and put \(G_j=f_j/f_1\). For
\(t_1<\cdots<t_k\),
\begin{equation}\label{eq:iterated-determinant}
 \det[f_j(t_i)]_{i,j=1}^k
 =\prod_{i=1}^k f_1(t_i)
 \int_{t_1}^{t_2}\!\cdots\!\int_{t_{k-1}}^{t_k}
 \det[G'_{j+1}(\tau_i)]_{i,j=1}^{k-1}
 \dd\tau_1\cdots\dd\tau_{k-1}.
\end{equation}
The identity may be applied repeatedly whenever the first member of the new
derivative family is positive.
\end{lemma}

\begin{proof}
Factor \(f_1(t_i)\) from row \(i\). The first column is then one. Replace
successive rows, from bottom to top, by their difference with the preceding
row. Each remaining entry is
\(G_j(t_{i+1})-G_j(t_i)=\int_{t_i}^{t_{i+1}}G_j'(\tau)\dd\tau\).
Determinant multilinearity gives \eqref{eq:iterated-determinant}. Since
\(\tau_i\in[t_i,t_{i+1}]\), the integration nodes remain ordered, so the same
argument applies to the derivative determinant.
\end{proof}

\begin{sloppypar}
Only the instances of Lemma~\ref{lem:quotient-integral} of sizes two through
four enter the theorem. The maintained formal engine proves exactly those
instances and the corresponding strict integral boxes; no arbitrary-order
quotient theorem is a premise of Theorem~\ref{thm:main}. In particular,
\path{PF4.FixedOrderQuotientWronskian.fixedOrderFour_quotientWronskian_package}
packages \eqref{eq:W3-quotient}--\eqref{eq:W4-third} together with the reversed
endpoint orientation \(p_4<p_3<p_2<p_1\). Its independent replay boundary is
\texttt{CERT29}.
\end{sloppypar}

\begin{lemma}[Confluent divided-difference limit]\label{lem:confluent-limit}
Let \(f\in C^{2k-2}\), let
\(V(a)=\prod_{0\leq i<j<k}(a_j-a_i)\), and let \(a,b\) be fixed strictly
increasing \(k\)-tuples. Then
\begin{equation}\label{eq:two-sided-confluence}
 \lim_{h\downarrow0}
 \frac{\det[f(z+h(a_i-b_j))]_{i,j=0}^{k-1}}
 {h^{k(k-1)}V(a)V(b)}
 =\frac{(-1)^{k(k-1)/2}}
 {\prod_{r=0}^{k-1}(r!)^2}
 \det[f^{(i+j)}(z)]_{i,j=0}^{k-1}.
\end{equation}
If only the row nodes coalesce while \(y_0<\cdots<y_{k-1}\) remain fixed,
then
\begin{equation}\label{eq:one-sided-confluence}
 \lim_{h\downarrow0}
 \frac{\det[f(z+ha_i-y_j)]_{i,j=0}^{k-1}}
 {h^{k(k-1)/2}V(a)}
 =\frac{\det[f^{(i)}(z-y_j)]_{i,j=0}^{k-1}}
 {\prod_{r=0}^{k-1}r!}.
\end{equation}
\end{lemma}

\begin{proof}
Apply successive Newton divided-difference row operations, whose divisors
are the positive numbers \(h(a_j-a_i)\), and let \(h\downarrow0\). This gives
\eqref{eq:one-sided-confluence}. Applying the same operation to the columns
gives derivatives with respect to \(-y\), hence the factor
\((-1)^{0+\cdots+(k-1)}\), and proves
\eqref{eq:two-sided-confluence}. This records the factorial normalization and
does not assume a nonzero leading coefficient.
\end{proof}

\begin{proposition}[Three-point equivalence]\label{prop:equivalence}
Under the strict lower-order positivity already proved, global \(\PF_4\) is
equivalent to
\[
 \partial_\xi\Psi(\xi;m,r)\leq0\qquad(\xi<m<r).
\]
Strict inequality implies strict global \(\PF_4\).
\end{proposition}

\begin{proof}
If \(\partial_\xi\Psi\leq0\), then \(p_4<p_3\) makes the right side of
\eqref{eq:L4-Psi} nonnegative. All prefactors in
\eqref{eq:W4-quotient} are positive. The Wronskian is therefore
nonnegative, and is positive in the strict case.

For clarity, applying Lemma~\ref{lem:quotient-integral} three times to the
order-four minor gives, with \(I_i=[t_i,t_{i+1}]\),
\begin{align*}
\det[u_j(t_i)]_{i,j=1}^4
={}&\prod_{i=1}^4u_1(t_i)
\int_{I_1\times I_2\times I_3}\prod_{i=1}^3v_2(\tau_i)\\
&\quad\times\int_{\tau_1}^{\tau_2}\int_{\tau_2}^{\tau_3}
w_3(\sigma_1)w_3(\sigma_2)
\int_{\sigma_1}^{\sigma_2}
\left(\frac{w_4}{w_3}\right)'(\rho)\dd\rho
\dd\sigma_2\dd\sigma_1\dd\boldsymbol\tau.
\end{align*}
Every factor is positive in the strict case, and every integration interval
has positive length. This proves positivity of every ordered collocation minor,
not only of the confluent Wronskian.

Conversely, assume global \(\PF_4\). Fix arbitrary
\(\xi_1<\xi_2<m<r\), choose any \(t\), and choose the columns so that
\((p_4,p_3,p_2,p_1)=(\xi_1,\xi_2,m,r)\) at \(t\); explicitly,
\(y_j=t-p_j\), which preserves \(y_1<\cdots<y_4\). Coalesce arbitrary
strictly ordered row nodes at \(t\). Equation
\eqref{eq:one-sided-confluence} and global \(\PF_4\) make the resulting
translate Wronskian nonnegative. Equations \eqref{eq:W4-quotient} and
\eqref{eq:L4-Psi} therefore give
\[
 \Psi(\xi_1;m,r)\geq\Psi(\xi_2;m,r).
\]
Because both the pair \(\xi_1<\xi_2\) and the pair \(m<r\) were arbitrary,
\(\Psi(\cdot;m,r)\) is nonincreasing for every admissible \(m,r\). Smoothness
makes this equivalent to the stated differential inequality.
\end{proof}
\section{Curvature coordinate and sign bridge}\label{sec:coordinate}

Since \(q>0\),
\[
 y(t)=-s(t),\qquad Q(y(t))=q(t)
\]
defines a global strictly increasing coordinate on its image, with
\(\dd y/\dd t=q(t)=Q(y)>0\). Primes in this and the next three sections mean
\(y\)-derivatives. Put
\[
 \rho=1-Q''=\frac{F_2}{q^3}>0,
 \qquad \kappa=2-Q''=1+\rho>1.
\]

For \(\xi<m<r\), write
\[
 p=y(\xi),\quad z=y(m),\quad w=y(r),\quad L=z-p,\quad R=w-z.
\]
Because \(A(a,b)=y(b)-y(a)\) and
\(M(a,b)=Q[y(a),y(b)]\),
\begin{equation}\label{eq:Lambda-coordinate}
 \Lambda=(w-p)+Q[p,z]-Q[z,w].
\end{equation}
Two integrations of \(\kappa=2-Q''\) give
\begin{align}
 \Lambda&=\frac1L\int_p^z(y-p)\kappa(y)\dd y
 +\frac1R\int_z^w(w-y)\kappa(y)\dd y,\label{eq:Lambda-triangular}\\
 \delta:=-\partial_p\Lambda
 &=\frac1{L^2}\int_p^z(z-y)\kappa(y)\dd y>0.
 \label{eq:delta-triangular}
\end{align}
Simultaneous translation becomes
\[
 \T=Q(p)\partial_p+Q(z)\partial_z+Q(w)\partial_w,
\]
and \(\partial_\xi=Q(p)\partial_p\). Thus
\(\Lambda_\xi=-Q(p)\delta\).

Define
\begin{equation}\label{eq:N-def}
 \mathcal N=\delta\Lambda^2+Q'(p)\delta\Lambda+
 \Lambda\T\delta-\delta\T\Lambda.
\end{equation}
Differentiating \(\Psi=\Lambda+\T\log\Lambda\), commuting simultaneous
translation with \(\partial_\xi\), and collecting over \(\Lambda^2\) gives
\begin{equation}\label{eq:sign-bridge}
 \partial_\xi\Psi=-\frac{Q(p)}{\Lambda^2}\mathcal N.
\end{equation}
Equivalently,
\begin{equation}\label{eq:K-def}
 \frac{\mathcal N}{\delta\Lambda}
 =K:=\Lambda+Q'(p)+\T\log\delta-\T\log\Lambda.
\end{equation}
It remains to prove \(K>0\).

\begin{sloppypar}
All objects here are defined only on the image of \(y=-s\).
\path{PF4.PaperObjectClosure.actualCoordinateRhoKappa_pos_on_range} proves the
displayed \(\rho,\kappa\) signs at every actual coordinate point, while
\path{PF4.SimultaneousCoordinateTranslation.actual_simultaneousCoordinateTranslation}
identifies literal simultaneous translation of the original endpoints with
the vector field \(\T\), including the derivative of the nonconstant
coefficient \(Q(p)\). Neither declaration extends \(Q\) by an assumed inverse
or asserts that the coordinate image is all of \(\mathbb R\).
\end{sloppypar}
\section{The confluent invariant in curvature form}\label{sec:confluent}

Define
\begin{equation}\label{eq:D-def}
 D=3(\kappa-1)-\{Q(\log\kappa)'\}'.
\end{equation}

\begin{lemma}[Confluent-to-curvature identity]\label{lem:C4-curvature}
The determinant \eqref{eq:C4-def} satisfies
\begin{equation}\label{eq:C4-curvature}
 \Cfour=Q^6\kappa^2D.
\end{equation}
Consequently \(D>0\) on \(\R\).
\end{lemma}

\begin{proof}
The change of variable gives \(\dd/\dd t=Q\dd/\dd y\) and \(c_2=-Q\).
Recursively applying this operator produces the five cumulants listed in
\appref{app:algebra}. Substitution into the Schur-complement form of
\eqref{eq:C4-def} factors out \(Q^6\). The remaining factor is
\[
 \kappa^2\left(3(\kappa-1)-\{Q(\log\kappa)'\}'\right),
\]
as shown by the common expanded numerator in \appref{app:algebra}. This proves
\eqref{eq:C4-curvature} without a numerical assumption. Lemma
\ref{lem:certified-input}, \(Q>0\), and \(\kappa>0\) then imply \(D>0\).
\end{proof}

The determinant definition is primary: it is the doubly confluent
fourth-order translation minor after division by the positive row and column
Vandermonde factors and by \(\Phi^4\). The explicit thirteen-term expansion is
included in \appref{app:algebra} for independent checking of the certificate
input.

\section{Exact endpoint transport identity}\label{sec:transport}

Write the three normalized triangular densities from
\eqref{eq:Lambda-triangular} and \eqref{eq:delta-triangular} as
\begin{align}
 \mu_L(y)&=\frac{(z-y)\kappa(y)}{L^2\delta}
 \quad(p\leq y\leq z),\label{eq:mu}\\
 \nu_L(y)&=\frac{(y-p)\kappa(y)}{L\Lambda}
 \quad(p\leq y\leq z),\nonumber\\
 \nu_R(y)&=\frac{(w-y)\kappa(y)}{R\Lambda}
 \quad(z\leq y\leq w).\label{eq:nu}
\end{align}
The triangular identities give
\begin{equation}\label{eq:density-masses}
 \int_p^z\mu_L=1,qquad
 \int_p^z\nu_L+\int_z^w\nu_R=1.
\end{equation}
No measure theory is needed below; these are normalized continuous weights on
compact intervals.

Set
\[
 A_0(y)=3(y-Q'(y))-Q(y)\frac{\kappa'(y)}{\kappa(y)}.
\]
Then \(A_0'=D\).

\begin{lemma}[Endpoint transport cancellation]\label{lem:transport}
With \(K\) as in \eqref{eq:K-def}, put
\begin{equation}\label{eq:transport-endpoint}
 \mathcal E=
 \frac{-I_L/L+I_R/R}{\Lambda}
 +\frac{L\mathcal H(p)-I_L}{L^2\delta},
\end{equation}
where \(I_L=\mathcal J(z)-\mathcal J(p)\) and
\(I_R=\mathcal J(w)-\mathcal J(z)\), with \(\mathcal H,\mathcal J\) defined
below. Then
\begin{equation}\label{eq:transport-expectation}
 K=\mathcal E.
\end{equation}
\end{lemma}

\begin{proof}
Two elementary primitives carry the complete cancellation:
\begin{align}
 \kappa A_0&=\mathcal H',&
 \mathcal H&=3y^2-3Q-3yQ'+(Q')^2+QQ'',\label{eq:H}\\
 \mathcal H&=\mathcal J',& \mathcal J&=y^3-3yQ+QQ'.\label{eq:J}
\end{align}
Both identities follow by one differentiation. Integrating the three linear
weights once by parts gives
\begin{equation}\label{eq:expectation-endpoint}
 \int_p^z A_0\nu_L+\int_z^w A_0\nu_R-\int_p^z A_0\mu_L
 =\mathcal E.
\end{equation}

On the other hand, differentiation of the triangular integrals along \(\T\)
gives
\[
 \T\Lambda=U(z,w)-U(p,z),
\quad
 \T\delta=\frac{U(p,z)-(Q(z)-Q(p))\delta-Q(p)\kappa(p)}L,
\]
where
\begin{equation}\label{eq:U-endpoint}
 U(c,d)=Q(c)+Q(d)-\frac{Q(d)Q'(d)-Q(c)Q'(c)}{d-c}
 +\frac{(Q(d)-Q(c))^2}{(d-c)^2}.
\end{equation}
Substitution in \eqref{eq:K-def} yields
\begin{equation}\label{eq:K-endpoint}
 K=\Lambda+Q'(p)-Q[p,z]
 +\frac{U(p,z)-U(z,w)}{\Lambda}
 +\frac{U(p,z)-Q(p)\kappa(p)}{L\delta}.
\end{equation}
The endpoint identity equating \eqref{eq:transport-endpoint} and
\eqref{eq:K-endpoint}, with every substitution exposed, is
\appref{app:endpoints}. It is an identity in the endpoint positions and the
values of \(Q,Q',Q''\); no bound, coordinate-surjectivity assertion, or
polynomial model is used.
\end{proof}

The normalized weights may independently be regarded as probability measures
\(\mu\) and \(\nu\). In that notation \eqref{eq:expectation-endpoint} says
\(\mathcal E=\mathbb E_\nu[A_0]-\mathbb E_\mu[A_0]\). This interpretation is
formally checked, but the deterministic proof in the next section uses only
the displayed compact-interval densities and their masses.
\section{The positive closed coordinate gap}\label{sec:crossing}

Define a deterministic piecewise function on \([p,w]\) by
\begin{equation}\label{eq:closed-gap}
 \Delta(y)=
 \begin{cases}
 \displaystyle
 \frac{-(z-y)^2-(z-y)Q'(y)-Q(y)+(z-p)^2+(z-p)Q'(p)+Q(p)}
      {L^2\delta}\\[3pt]
 \displaystyle\qquad
 -\frac{(y-p)^2-(y-p)Q'(y)+Q(y)-Q(p)}{L\Lambda},
 &p\leq y\leq z,\\[12pt]
 \displaystyle
 \frac{(w-y)^2+(w-y)Q'(y)+Q(y)-Q(w)}{R\Lambda},
 &z<y\leq w.
 \end{cases}
\end{equation}
The fundamental theorem of calculus and \(\kappa=2-Q''\) identify these
closed expressions with
\begin{equation}\label{eq:gap-integrals}
 \Delta(y)=
 \begin{cases}
 \displaystyle\int_p^y(\mu_L(t)-\nu_L(t))\dd t,&p\leq y\leq z,\\[6pt]
 \displaystyle\int_y^w\nu_R(t)\dd t,&z<y\leq w.
 \end{cases}
\end{equation}
The two branches agree at \(z\) by \eqref{eq:density-masses}.

\begin{lemma}[Strict closed gap]\label{lem:crossing}
The function \(\Delta\) is continuous on \([p,w]\), satisfies
\(\Delta(p)=\Delta(w)=0\), and
\[
 \Delta(y)>0\qquad(p<y<w).
\]
\end{lemma}

\begin{proof}
The endpoints and continuity follow from \eqref{eq:closed-gap},
\eqref{eq:gap-integrals}, and the exact mass identities. On \((p,z)\), the
difference of the positive left densities changes sign at the explicit strict
convex combination
\[
 y_* = \frac{\Lambda z+L\delta p}{\Lambda+L\delta}\in(p,z).
\]
Indeed, clearing the positive common factor \(\kappa(y)\) and the positive
denominators gives
\[
 \mu_L(y)-\nu_L(y)>0\iff y<y_*,
 \qquad
 \mu_L(y)-\nu_L(y)<0\iff y>y_*.
\]
Thus \(\Delta(y)>0\) for \(p<y\leq y_*\). For \(y_*\leq y\leq z\), subtract
the two identities in \eqref{eq:density-masses} and split at \(y\) to obtain
\[
 \Delta(y)=\int_y^z(\nu_L-\mu_L)\dd t+\int_z^w\nu_R\dd t>0.
\]
The first integral is nonnegative and the second is strictly positive because
\(z<w\), \(\kappa>0\), and \(\Lambda>0\). On \((z,w)\), positivity follows
directly from the positive tail integral in \eqref{eq:gap-integrals}.
\end{proof}

On the left branch \(\Delta'=\mu_L-\nu_L\), and on the right branch
\(\Delta'=-\nu_R\). Direct integration by parts on \([p,z]\) and \([z,w]\),
using \(A_0'=D\), the zero endpoint values, and the equality of the two
branches at \(z\), gives
\begin{align}
 \int_p^w\Delta(y)D(y)\dd y
 &=\int_p^zA_0\nu_L+\int_z^wA_0\nu_R-\int_p^zA_0\mu_L\nonumber\\
 &=\mathcal E=K.\label{eq:crossing-integral}
\end{align}
Combining \eqref{eq:K-def}, \eqref{eq:C4-curvature}, and
\eqref{eq:crossing-integral} gives the central identity
\begin{equation}\label{eq:central-identity}
 \mathcal N=\delta\Lambda\int_p^w
 \Delta(y)\frac{\Cfour(y)}{Q(y)^6\kappa(y)^2}\dd y>0.
\end{equation}
Every factor in the interior is strictly positive.

The probability interpretation is optional: the same \(\Delta\) is
\(F_\mu-F_\nu\), and the density ratio has one crossing. The proof above does
not require probability instances, CDF complement identities, endpoint ratio
limits, or a separate existence-and-uniqueness argument for that crossing.
\begin{sloppypar}
The maintained declarations
\path{PF4.GlobalStrictPF4.globalRiemannKernel_coordinateNumerator_pos} and
\path{PF4.GlobalStrictPF4.globalRiemannKernel_coordinatePartialXiPsi_neg}
export, for the literal Riemann kernel and every \(\xi<m<r\), respectively the
strict positivity in \eqref{eq:central-identity} and the negative derivative
in \eqref{eq:sign-bridge}. All coordinate points in these statements lie in
the actual image of \(y=-s\); no surjectivity onto \(\mathbb R\) is asserted.
\end{sloppypar}
\section{Completion and exact order}\label{sec:completion}

Equation \eqref{eq:sign-bridge} and \eqref{eq:central-identity} imply
\[
 \partial_\xi\Psi(\xi;m,r)<0\qquad(\xi<m<r).
\]
Proposition~\ref{prop:equivalence} therefore proves part~(1) of
Theorem~\ref{thm:main}.

We now prove directly that the classification stops at order four. Let
\(h=211/2000\). Exact rational theta enclosures give
\begin{equation}\label{eq:finite-pf5-witness}
 -1.08\mathbin{\cdot}10^{-7}
 <\det[\Phi((i-j)h)]_{i,j=0}^4
 <-1.05\mathbin{\cdot}10^{-7}.
\end{equation}

\begin{theorem}\label{thm:not-pf5}
The Riemann kernel is not \(\PF_5\).
\end{theorem}

\begin{proof}
The nodes \(0,h,2h,3h,4h\) are strictly increasing. Evenness identifies the
translation matrix with the symmetric Toeplitz matrix determined by the five
kernel values \(\Phi(0),\Phi(h),\ldots,\Phi(4h)\). Each value is enclosed by
exact Taylor bounds for the retained theta modes and the maintained infinite
tail theorem; a rational determinant parity factorization then gives
\eqref{eq:finite-pf5-witness}. This is a negative translation minor at
distinct nodes, with no limiting argument.

\begin{sloppypar}
In the formal development the node ordering, signed-index orientation,
Toeplitz identification, value boxes, determinant sign, and primary-kernel
identity are all premises of
\path{PF4.globalRiemannKernel_orderFive_translationMinor_neg}. Thus the
order-five obstruction used by Theorem~\ref{thm:main} does not depend on the
confluent calculations below.
\end{sloppypar}
\end{proof}

\subsection*{Optional confluent structure}

The origin and threshold calculations give independent information about the
first order-five failure, but are not used in the exact-order assembly. Put
\[
 \mathsf H_k=\det[\Phi^{(i+j)}(0)]_{i,j=0}^{k-1},\qquad
 s_j=\Phi^{(j)}(0).
\]
Since \(\Phi\) is even, simultaneous parity permutations of the rows and
columns give
\[
 \mathsf H_4=AB,\qquad \mathsf H_5=CB,
\]
where
\[
 A=s_0s_4-s_2^2,\qquad B=s_2s_6-s_4^2,
\]
and
\[
 C=\det\begin{pmatrix}
 s_0&s_2&s_4\\
 s_2&s_4&s_6\\
 s_4&s_6&s_8
 \end{pmatrix}.
\]

\begin{lemma}\label{lem:origin-pf5-sign}
For the Riemann kernel,
\[
 445<A<446,\qquad 189223<B<189228,
 \qquad -674000000<C<-614000000.
\]
In particular, \(\mathsf H_4>0\) and \(\mathsf H_5<0\).
\end{lemma}

\begin{proof}
For \(x=\pi n^2e^{2u}\), the \(n\)-th summand of \(\Phi(u)\) is
\(e^{u/2-x}T_0(x)\), where \(T_0(x)=2x(2x-3)\). If its \(j\)-th derivative
is \(e^{u/2-x}T_j(x)\), then
\[
 T_{j+1}=2xT_j'+(1/2-2x)T_j.
\]
Thus
\[
 s_j=\sum_{n\ge1}e^{-\pi n^2}T_j(\pi n^2).
\]
The first three modes are enclosed by rational alternating-series bounds.
Machin's identity
\(\pi=16\arctan(1/5)-4\arctan(1/239)\) supplies rational bounds for \(\pi\),
and argument division followed by the degree-29 and degree-30 alternating
Taylor sums supplies rational bounds for each exponential.

For the omitted modes, let \(S_j\) be the sum of the absolute coefficients of
\(T_j\). Since \(\deg T_j=j+2\), \(3<\pi<22/7\), and
\(e^3>\sum_{r=0}^8 3^r/r!>20\),
\[
 \sum_{n\ge4}|T_j(\pi n^2)|e^{-\pi n^2}
 \leq
 \frac{S_j(22/7)^{j+2}4^{2j+4}20^{-16}}
 {1-(5/4)^{20}20^{-9}}
 \qquad(j=0,2,4,6,8).
\]
All endpoints lie on \(10^{-36}\mathbb Z\), and every arithmetic operation is
rounded outward. Substitution into the displayed formulas gives the entirely
rational sign chain
\[
 0<445<A<446,\qquad 0<189223<B<189228,
\]
\[
 -674000000<C<-614000000<0.
\]
Thus \(AB>0\) and \(CB<0\) without a floating-point determinant. The full
grid endpoints and the standard-library verifier are included in the
reproducibility archive.
\end{proof}

Applying Lemma~\ref{lem:confluent-limit} with \(k=5\), \(z=0\), and
\(a_i=b_i=i\) shows independently that
\(\det[\Phi((i-j)\varepsilon)]_{i,j=0}^4<0\) for every sufficiently small
positive \(\varepsilon\). This implication is not needed for
Theorem~\ref{thm:not-pf5}, whose witness is the fixed rational spacing above.

For the equal-step family put
\[
 D_5(u,h)=\det[\Phi(u+(i-j)h)]_{i,j=0}^4,\qquad
 C_5(u)=\lim_{h\downarrow0}\frac{D_5(u,h)}{h^{20}}.
\]
Because \(V(0,\ldots,4)=\prod_{j=1}^4j!\), the Vandermonde and factorial
factors in Lemma~\ref{lem:confluent-limit} cancel, and therefore
\begin{equation}\label{eq:C5-H5}
 C_5(u)=\det[\Phi^{(i+j)}(u)]_{i,j=0}^4.
\end{equation}

\begin{theorem}[Confluent order-five threshold]\label{thm:confluent-threshold}
There is a unique \(u_*>0\) such that \(C_5(u_*)=0\), and
\[
 0.0622795266356<u_*<0.0622795266357.
\]
Moreover \(C_5(u)<0\) for \(0\leq u<u_*\), while \(C_5(u)>0\) for
\(u>u_*\).
\end{theorem}

\begin{proof}
Put \(x=\pi e^{2u}\), \(y=e^{-3x}\), and \(z=e^{-8x}\). After removing the
positive first-mode amplitude \(2xe^{5u/2-x}\), the first three theta modes of
the derivative jet are
\[
 b_j=P_j(x)+4yP_j(4x)+9zP_j(9x),
\]
where
\[
 P_0(x)=2x-3,\qquad
 P_{j+1}(x)=\left(\frac52-2x\right)P_j(x)+2xP_j'(x).
\]
Thus the three-mode part of \(C_5\), apart from a positive fifth power, is the
closed determinant
\begin{equation}\label{eq:three-mode-C5}
 G_3(x,y,z)=\det[b_{i+j}]_{i,j=0}^4.
\end{equation}
Its exact expansion has 231 monomials. The path derivative is obtained without
another expansion from
\[
 \frac{d}{du}=2x(\partial_x-3y\partial_y-8z\partial_z).
\]

For \(j\leq9\), the omitted modes satisfy
\begin{equation}\label{eq:C5-tail}
 |e_j(x)|\leq
 \frac{S_jx^{j+1}4^{2j+4}e^{-15x}}
 {1-(5/4)^{22}e^{-9x}},
\end{equation}
where \(S_j\) is the sum of the absolute coefficients of \(P_j\). Exact
rational Bernstein bounds, preserving the common \(x\)-dependence of
\(e^{-3x}\) and \(e^{-8x}\), give \(C_5<0\) from \(u=0\) through \(u=1/50\)
and \(C_5'>0\) on the overlapping range from \(u=3/200\) through \(x=4\).
Direct four-mode endpoint enclosures give opposite signs at
\(u=0.0622795266356\) and \(u=0.0622795266357\). Four further Bernstein cells
give \(C_5>0\) for \(4\leq x\leq40\), and the exact one-mode determinant plus
\eqref{eq:C5-tail} gives positivity for \(x\geq40\). These overlapping signs
prove existence, uniqueness, and the stated classification. The domains and
cell counts are listed in \appref{app:pf5-threshold}.
\end{proof}

The outermost center over all finite spacings is a separate two-variable
extremal problem; no such global extremality is used here.

Equation~\eqref{eq:finite-pf5-witness} proves part~(2) of
Theorem~\ref{thm:main}. Together with the strict minors through order four,
this completes the exact-order classification. The preceding confluent
theorem is not used in that assembly.

\begin{remark}[Riemann Hypothesis boundary]
Schoenberg's transform theorem says that the bilateral Laplace transform of a
\(\PF_\infty\) function is the reciprocal of a Laguerre--P\'olya entire function
on its strip of convergence~\cite{schoenberg-ii,belton}. The Fourier transform
of \(\Phi\), up to the standard normalization, is the Riemann \(\Xi\)-function,
which has known real zeros; hence \(\Phi\) is unconditionally not
\(\PF_\infty\). The Schoenberg formulation related to the Riemann Hypothesis
instead asks for the inverse transform of the reciprocal of \(\Xi\) to be a
P\'olya-frequency function~\cite{grochenig}. Thus the finite-order classification
proved here is a different statement. The next section further shows that
strict \(\PF_4\) alone does not imply Fourier real-rootedness.
\end{remark}
\section{An explicit continuous \texorpdfstring{$\PF_4$}{PF4} separator}
\label{sec:separator}

We now prove Theorem~\ref{thm:separator}.  Put
\[
 c=\frac1{64},\qquad
 B(w)=\sum_{k=-3}^{3}b_kw^k,\qquad
 (b_{-3},\ldots,b_3)=(2,10,23,30,23,10,2),
\]
and define
\begin{equation}\label{eq:separator-kernel}
 f_*(x)=e^{-cx^2}B(e^{2cx})
 =\sum_{k=-3}^{3}b_ke^{ck^2}e^{-c(x-k)^2}.
\end{equation}
The Gaussian-mixture expression proves positivity and Schwartz decay;
palindromy of \((b_k)\) proves evenness.

\subsection{Strict \texorpdfstring{$\PF_3$}{PF3}}

For fixed \(x\), give \(\mathsf X\in\{-3,\ldots,3\}\) probability
proportional to \(b_ke^{2ckx}\), and write \(\chi_j\) for its cumulants.
Differentiation of
the finite log-partition function gives
\begin{equation}\label{eq:separator-cumulants}
 q=2c-(2c)^2\chi_2,\qquad
 q'=-(2c)^3\chi_3,\qquad
 q''=-(2c)^4\chi_4.
\end{equation}
If \(\bar x=\mathbb E\mathsf X\), then
\(0\leq\mathbb E[(\mathsf X+3)(3-\mathsf X)]=9-\chi_2-\bar x^2\).
Thus \(0\leq\chi_2\leq9\), and hence
\begin{equation}\label{eq:separator-q}
 q\geq2c(1-18c)=2c\frac{23}{32}>0.
\end{equation}
Moreover,
\begin{align}
 F_2
 &=q^3-\{qq''-(q')^2\}\notag\\
 &=q^3+q(2c)^4\chi_4+(2c)^6\chi_3^2.       \label{eq:separator-f2}
\end{align}
The identity
\(\chi_4=\mathbb E(\mathsf X-\mathbb E\mathsf X)^4-3\chi_2^2\) gives
\(\chi_4\geq-243\). Dropping the final nonnegative term in
\eqref{eq:separator-f2} gives
\[
 F_2\geq q\{q^2-3888c^4\}.
\]
At \(c=1/64\), the two coefficients after division by \(c^2\) are
\[
 q^2/c^2\geq\frac{529}{256},\qquad
 3888c^2=\frac{243}{256}.
\]
Thus \(F_2\geq q c^2(143/128)>0\) globally.  The weighted-mean criterion of
\secref{sec:pf3} proves strict \(\PF_3\).

\subsection{Exact order-four density}

Let \(\epsilon=2c=1/32\), \(t=e^{\epsilon x}\), and
\[
 P(t)=t^3B(t)=2+10t+23t^2+30t^3+23t^4+10t^5+2t^6.
\]
For \(E=t\frac{\dd}{\dd t}\), define
\begin{equation}\label{eq:separator-N-recurrence}
 N_1=tP',\qquad N_{j+1}=t(N_j'P-jN_jP').
\end{equation}
The quotient rule gives \(E^j\log P=N_j/P^j\). Therefore, for
\(\ell_j=(\log f_*)^{(j)}\),
\begin{equation}\label{eq:separator-logjets}
 \ell_2=\frac{-\epsilon P^2+\epsilon^2N_2}{P^2},
 \qquad
 \ell_j=\frac{\epsilon^jN_j}{P^j}\quad(3\leq j\leq6).
\end{equation}
Insert these jets into the central-moment determinant
\eqref{eq:C4-def}. Every monomial has derivative weight twelve, so every
term may first be put over the common denominator \(P^{12}\). The resulting
numerator has the exact factor \(P^8\). After cancellation,
\begin{equation}\label{eq:separator-c4}
 \Cfour[f_*](x)=\frac{\mathcal G(t)}{2^{54}P(t)^4}.
\end{equation}
The exact expansion printed in \appref{app:separator} proves that
\(\mathcal G\) is palindromic of degree 24 and that all 25 integer
coefficients are strictly positive. Hence \(\Cfour[f_*]>0\) on \(\R\).

The established inequalities \(q>0\) and \(F_2>0\) also give
\[
 \kappa=2-Q''=\frac{q^3+F_2}{q^3}>0.
\]
The generic transport identity \eqref{eq:central-identity} now has strictly
positive density and crossing weight for \(f_*\).  Thus
\(\partial_\xi\Psi<0\), and Proposition~\ref{prop:equivalence} proves that
\(f_*\) is strict \(\PF_4\).

\subsection{Nonreal Fourier zeros}

With \(\widehat f(z)=\int_\R f(x)e^{-izx}\dd x\), Gaussian translation gives
\begin{equation}\label{eq:separator-fourier}
 \widehat f_*(z)=\sqrt{\frac{\pi}{c}}e^{-z^2/(4c)}
 \sum_{k=-3}^{3}b_ke^{ck^2}e^{-ikz}.
\end{equation}
Put \(w=e^{-iz}\) and \(u=w+w^{-1}\).  The Laurent factor in
\eqref{eq:separator-fourier} vanishes exactly when
\begin{equation}\label{eq:separator-cubic}
 R_c(u)=2e^{9c}u^3+10e^{4c}u^2
 +(23e^c-6e^{9c})u+30-20e^{4c}
\end{equation}
vanishes. At \(c=1/64\), the exact calculation in
\appref{app:separator} gives \(\operatorname{disc}(R_c)<0\). Thus the real
cubic has a nonreal conjugate pair.
For \(|w|=1\), however, \(w+w^{-1}\) is real. The corresponding \(w\)-roots
therefore lie off the unit circle and lift through \(w=e^{-iz}\) to zeros
with \(\operatorname{Im}z\neq0\). The Gaussian factor is zero-free. This
completes the proof of Theorem~\ref{thm:separator}.
\section{Exact verification and reproduction}\label{sec:reproducibility}

The primary universal theorem is checked by the pinned Lean project in
\path{proof/formal}. Running \texttt{lake build} constructs the real theta
series, the analytic kernel and global derivative jet, the universal cleared
signs, the arbitrary-node strict minors through order four, and the exact
negative order-five witness. Running
\texttt{lake env lean PF4/Audit.lean} prints the axiom dependencies of the
exported declarations. They are exactly the standard Lean/mathlib axioms
\texttt{propext}, \texttt{Classical.choice}, and \texttt{Quot.sound}; the
dependency tree contains no \texttt{sorry}, \texttt{admit}, custom axiom, or
unsafe theorem bridge.

The repository supplies independent verifiers for the finite algebra and
rational inequalities used above.
\begin{center}
\small
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.25\textwidth}
>{\raggedright\arraybackslash}p{0.47\textwidth}
>{\raggedright\arraybackslash}p{0.19\textwidth}@{}}
\toprule
Object & Repository verifier & Arithmetic \\
\midrule
Global \(q,F_2,\Cfour\) &
\path{scripts/verify_riemann_signs_exact.py} & rational polynomial \\
Quotient reduction &
\path{scripts/verify_pf4_wronskian_reduction.py} & symbolic exact \\
Transport identity &
\path{scripts/verify_pf4_transport_kernel.py} & symbolic exact \\
Origin order-five sign &
\path{scripts/verify_pf5_origin.py} & rational enclosures \\
Three-mode order-five polynomial &
\texttt{scripts/verify\_pf5\_threshold\_symbolic.py} & symbolic exact \\
Order-five threshold and witness &
\path{scripts/verify_pf5_threshold.py} & rational Bernstein \\
Continuous separator &
\texttt{scripts/verify\_continuous\_pf4\_separator.py} & rational polynomial \\
\bottomrule
\end{tabular}
\end{center}

The global-sign verifier retains the first two theta modes exactly. It checks
the 361 Bernstein and decay inequalities summarized in \appref{app:tail}, the
140 derivative-envelope coefficients, and the analytic geometric bounds for
all modes \(n\geq3\). Its launcher selects SymPy's pure-Python rational domain
and refuses a FLINT import. No floating-point comparison or interval
subdivision decides a sign.

The origin order-five verifier is independent of that calculation. It uses integer
arithmetic with outward rounding on \(10^{-36}\mathbb Z\), Machin bounds for
\(\pi\), alternating Taylor bounds for three theta modes, and the geometric
tail in Lemma~\ref{lem:origin-pf5-sign}. The threshold verifiers reconstruct
the 231-monomial three-mode determinant, certify the unique crossing by
correlated rational Bernstein cells, and directly enclose
\eqref{eq:finite-pf5-witness}. The separator verifier reconstructs
the central determinant, checks the exact \(P^8\) cancellation, verifies all
25 coefficients in \eqref{eq:separator-c4}, and reproduces the rational
discriminant inequality in \appref{app:separator}. The generated coefficient
record has SHA-256
\begin{center}
\texttt{d0f91259919c7f237ef65068041122656636ca990fe6ef41a146dd53eaa1dba9}.
\end{center}

The quotient and transport scripts check identities for generic smooth jets.
Their numerical evaluations at selected points are regression tests only; all
sign conclusions follow from the displayed identities and exact inequalities.

From a clean checkout with Python 3.13, SymPy 1.14.0, and mpmath 1.3.0, the
single replay command is
\begin{center}
\texttt{python scripts/replay\_paper.py}.
\end{center}
It prints one line beginning \texttt{PASS} for each certificate boundary, followed
by \texttt{status=paper evidence replay passed}. The SHA-256 of its complete
standard output is
\begin{center}
\texttt{5204f9fa12bf539edc245c257db285ab42e2041e4735f782a84852e5c7f0a592}.
\end{center}
Package versions and the complete artifact hashes are also recorded in
\path{requirements-paper.txt} and \path{paper/RELEASE_MANIFEST.md}.
\section{Declarations, availability, and computational provenance}

\paragraph{Author contribution.}
Joshuah Rainstar conceived and directed the project, developed the proof
architecture, verified the exact computations, and prepared
the manuscript.

\paragraph{Acknowledgments and computational assistance.}
The author acknowledges the use of OpenAI Codex and ChatGPT, Anthropic Claude,
and Moonshot AI Kimi for symbolic calculation, implementation, drafting, and
review. The author takes responsibility for the mathematical claims and the
final manuscript.

\paragraph{Conflict of interest.}
The author declares no competing interests.

\paragraph{Code and data availability.}

The public repository is
\url{https://github.com/falseywinchnet/zeta}. The exact analytic proof was
promoted in commit
\href{https://github.com/falseywinchnet/zeta/commit/8a4db9e24b3a47a3eb4d35b89eb1a3f8e80eab9d}{\texttt{8a4db9e24b3a}}.
That immutable snapshot contains the submission source, coefficient records,
environment lock, replay tool, and PDF; their SHA-256 values are listed in
\path{paper/RELEASE_MANIFEST.md}. The complete repository release is assigned
the DOI \url{https://doi.org/10.5281/zenodo.21404360}. The complete evidence replay is
\texttt{python scripts/replay\_paper.py} from the repository root.

All theorem-bearing sign decisions are exact. Numerical values produced by
the repository scripts are diagnostic only; there is no separate experimental
dataset.
\clearpage
\begin{thebibliography}{99}
\bibitem{schoenberg-ii}
I. J. Schoenberg,
\emph{On P\'olya frequency functions. II. Variation-diminishing integral
operators of the convolution type},
Acta Sci. Math. (Szeged) \textbf{12} (1950), 97--106.

\bibitem{karlin}
S. Karlin,
\emph{Total Positivity, Vol. I},
Stanford University Press, Stanford, 1968.

\bibitem{belton}
A. Belton, D. Guillot, A. Khare, and M. Putinar,
\emph{Preservers of totally positive kernels and P\'olya frequency functions},
Math. Res. Rep. \textbf{3} (2022), 35--56,
arXiv:2110.08206.

\bibitem{khare}
A. Khare,
\emph{Multiply positive functions, critical exponent phenomena, and the
Jain--Karlin--Schoenberg kernel},
arXiv:2008.05121.

\bibitem{debruijn}
N. G. de Bruijn,
\emph{The roots of trigonometric integrals},
Duke Math. J. \textbf{17} (1950), 197--226,
doi:10.1215/S0012-7094-50-01720-0.

\bibitem{dimitrov-xu}
D. K. Dimitrov and Y. Xu,
\emph{Wronskians of Fourier and Laplace transforms},
Constr. Approx. \textbf{48} (2018), 55--99,
arXiv:1606.05011.

\bibitem{csordas-varga}
G. Csordas and R. S. Varga,
\emph{Moment inequalities and the Riemann Hypothesis},
Constr. Approx. \textbf{4} (1988), 175--198,
doi:10.1007/BF02075457.

\bibitem{grochenig}
K. Grochenig,
\emph{Schoenberg's theory of totally positive functions and the Riemann zeta
function},
arXiv:2007.12889.

\bibitem{michalowski}
W. Micha\l{}owski,
\emph{On the P\'olya frequency order of the de Bruijn--Newman kernel:
certified failure at order five and the Toeplitz threshold phenomenon},
arXiv:2602.20313.
\end{thebibliography}

\appendix
\section{Confluent and curvature algebra}\label{app:algebra}

The central-moment Hankel matrix is
\[
 \begin{pmatrix}
 1&0&m_2&m_3\\
 0&m_2&m_3&m_4\\
 m_2&m_3&m_4&m_5\\
 m_3&m_4&m_5&m_6
 \end{pmatrix}.
\]
Taking the Schur complement of the upper-left entry reduces its determinant to
\[
 \det\begin{pmatrix}
 m_2&m_3&m_4\\
 m_3&m_4-m_2^2&m_5-m_2m_3\\
 m_4&m_5-m_2m_3&m_6-m_3^2
 \end{pmatrix}.
\]
Substitution of the moments from \secref{sec:inputs} and ordinary
three-by-three expansion gives
\begin{align}\label{eq:C4-expanded}
\Cfour={}&12c_2^6+24c_2^4c_4-24c_2^3c_3^2+2c_2^3c_6
-12c_2^2c_3c_5+7c_2^2c_4^2\\
&+12c_2c_3^2c_4+c_2c_4c_6-c_2c_5^2-9c_3^4-c_3^2c_6
+2c_3c_4c_5-c_4^3.
\end{align}

In the curvature coordinate, repeated application of
\(Q\dd/\dd y\) to \(c_2=-Q\) gives
\begin{align*}
c_2={}&-Q,\\
c_3={}&-QQ',\\
c_4={}&-Q\{(Q')^2+QQ''\},\\
c_5={}&-Q\{(Q')^3+4QQ'Q''+Q^2Q'''\},\\
c_6={}&-Q\{(Q')^4+11Q(Q')^2Q''+4Q^2(Q'')^2
 +7Q^2Q'Q'''+Q^3Q''''\}.
\end{align*}
Substitution in the preceding polynomial gives
\[
 \Cfour=-Q^6\mathcal P,
\]
where
\begin{align*}
\mathcal P={}&QQ''Q''''-Q(Q''')^2-2QQ''''+Q'Q''Q'''-2Q'Q'''\\
&+3(Q'')^3-15(Q'')^2+24Q''-12.
\end{align*}
Now \(\kappa=2-Q''\), and direct differentiation gives
\[
 \{Q(\log\kappa)'\}'
 =\frac{Q'\kappa'+Q\kappa''}{\kappa}
  -\frac{Q(\kappa')^2}{\kappa^2},
\]
so, after multiplication by \(\kappa^2\) and substitution of
\(\kappa'= -Q'''\), \(\kappa''=-Q''''\),
\[
 3(\kappa-1)-\{Q(\log\kappa)'\}'
 =-\frac{\mathcal P}{(Q''-2)^2}
 =-\frac{\mathcal P}{\kappa^2}.
\]
Therefore \(\Cfour=Q^6\kappa^2D\), proving
\eqref{eq:C4-curvature} by an exposed common numerator.
\section{Exact proof of the certified input}\label{app:tail}

This appendix proves Lemma~\ref{lem:certified-input}. The positive-side
theta series has \(j\)-th derivative
\[
 2\pi n^2e^{5u/2-n^2x}R_j(n^2x),\qquad x=\pi e^{2u},
\]
where the polynomials \(R_j\) satisfy the recurrence in
\secref{sec:inputs}. Machin's identity and alternating series give
\(\pi>157/50\); hence \(R_0(x)=2x-3>0\).
The same recurrence, exponential bounds, compact Bernstein margins, and
infinite-tail reduction are encoded in the maintained Lean modules
\path{PF4.CERT12CompactClosure} and \path{PF4.CERT12OuterClosure}. The formulas
below remain the human-readable certificate and the independent exact-Python
replay.

\subsection{Cleared sign polynomials}

In addition to \(a_j\), define the normalized remaining modes
\[
 e_j(x)=\sum_{n\geq3}
 \frac{n^2e^{-(n^2-1)x}R_j(n^2x)}{R_0(x)},
 \qquad \widehat a_j=a_j+e_j.
\]
For an indeterminate raw jet \((\widehat a_0,\ldots,\widehat a_6)\), put
\[
 N_q=\widehat a_1^2-\widehat a_0\widehat a_2,
\]
\begin{align*}
N_{F_2}={}&-\widehat a_0^4\widehat a_2\widehat a_4
+\widehat a_0^4\widehat a_3^2
+\widehat a_0^3\widehat a_1^2\widehat a_4
-2\widehat a_0^3\widehat a_1\widehat a_2\widehat a_3
+2\widehat a_0^3\widehat a_2^3\\
&-3\widehat a_0^2\widehat a_1^2\widehat a_2^2
+3\widehat a_0\widehat a_1^4\widehat a_2-\widehat a_1^6,
\end{align*}
and
\[
 N_{\Cfour}=\det[\widehat a_{i+j}]_{i,j=0}^3.
\]
Direct logarithmic differentiation and the central-moment determinant give
\begin{equation}\label{eq:raw-signs}
 q=\frac{N_q}{\widehat a_0^2},\qquad
 F_2=\frac{N_{F_2}}{\widehat a_0^6},\qquad
 \Cfour=\frac{N_{\Cfour}}{\widehat a_0^4}.
\end{equation}
The thirteen-term cumulant expansion obtained from the last identity agrees
with \eqref{eq:C4-expanded}; this is an exact polynomial identity.

For orientation, retaining only the first mode gives
\[
q_1=\frac{4x(4x^2-12x+15)}{(2x-3)^2},
\]
\[
(F_2)_1=\frac{64x^3(64x^6-576x^5+2448x^4-6432x^3
+10044x^2-8100x+2295)}{(2x-3)^6},
\]
\[
(\Cfour)_1=\frac{49152x^6(16x^4-96x^3+360x^2-840x+945)}{(2x-3)^4}.
\]
After \(x=5+z\), every numerator has positive coefficients. The second
mode is retained exactly because it supplies the larger margin near the
origin.

\subsection{Exact two-mode margin}

Rational Taylor bounds for the exponential imply
\[
 0<\eta<\frac1{12000}\quad(x\geq\pi),
\]
and
\[
 \frac1{23000}<\eta<\frac1{12000}
 \quad\left(\frac{157}{50}\leq x\leq\frac{10}{3}\right).
\]
The close endpoints are entirely rational checks. Namely,
\[
 \sum_{k=0}^{16}\frac{(471/50)^k}{k!}>12000,\qquad
 \sum_{k=0}^{21}\frac{10^k}{k!}>22000,
\]
and the geometric bound for the tail after degree \(13\) gives
\[
 e^{10}<
 \sum_{k=0}^{13}\frac{10^k}{k!}
 \frac{10^{14}/14!}{1-10/15}
 =\frac{3480060751}{154791}<23000.
\]
These prove, respectively, the upper \(\eta\)-cap, the cap
\(e^{-10}<1/22000\), and the lower bound \(e^{-10}>1/23000\).
Likewise \(\sum_{k=0}^{21}15^k/k!>3{,}000{,}000\), which gives
\(\eta<1/3{,}000{,}000\) for \(x\geq5\).
We use the following elementary certificate lemma. If
\(p(s,t)=\sum p_{ij}s^it^j\) has bidegree \((d,e)\), its Bernstein
coefficients on the unit square are
\[
 \beta_{k\ell}=\sum_{i\leq k,\,j\leq\ell}
 p_{ij}\frac{\binom{k}{i}}{\binom{d}{i}}
       \frac{\binom{\ell}{j}}{\binom{e}{j}}.
\]
The power-to-Bernstein identity proves that \(\beta_{k\ell}>0\) for every
\(k,\ell\) implies \(p>0\) on the square.

Apply this lemma after affine rational changes of variables. For \(q\), one
rectangle ends at \(x=10/3\), followed by a positive base polynomial minus
exponentially decreasing corrections. For \(F_2\), dependent bounds on the
first rectangle are followed by a rectangle through \(x=5\) and a positive
half-strip expansion. For \(\Cfour\), the first rectangle is followed by two
negative odd-power corrections whose ratios to the positive base decrease.
The derivative of each ratio has a numerator with positive coefficients after
the indicated shift. The 361 resulting rational coefficient inequalities give
\begin{equation}\label{eq:two-mode-margin}
 q_{1,2}>10,\qquad (F_2)_{1,2}>1000,\qquad
 (\Cfour)_{1,2}>50{,}000{,}000.
\end{equation}
This is a finite algebraic proof on fixed domains.

Here is the precise connection between those coefficient checks and the
quantitative margins. Evaluate the raw polynomials at the two-mode jet and set
\[
 \mathcal Q=N_q-10a_0^2,
 \qquad \mathcal F=N_{F_2}-1000a_0^6,
 \qquad \mathcal C=N_{\Cfour}-50{,}000{,}000a_0^4.
\]
The rows labelled \(Q,F,C\) below certify the cleared numerators of
\(\mathcal Q,\mathcal F,\mathcal C\), respectively. Thus their positivity is
exactly, rather than merely qualitatively, the three inequalities in
\eqref{eq:two-mode-margin}. For a ratio row, write the shifted target as
\(B_0(x)+\sum_{j\geq1}\eta^jB_j(x)\), where \(B_0\) has positive shifted
coefficients. Whenever \(B_j\) is adverse, put \(D_j=-B_j\). Positivity of
\[
 3jD_jB_0-D_j'B_0+D_jB_0'
\]
after the same shift proves that
\(e^{-3jx}D_j(x)/B_0(x)\) decreases. The displayed endpoint ratio is the sum
of all such adverse ratios at the left endpoint; being less than one proves
the target positive on the entire half-line. Coefficientwise nonnegative
pieces only increase it.

For reference, the complete finite certificate is summarized below.  Write
\(\mathcal A=(2x-3)+4(8x-3)\eta\), which is positive on every listed domain.
Rows \(Q_0,F_0,F_1,C_0\) are Bernstein certificates after the indicated
affine change to the unit square; the remaining rows use coefficient
positivity after a half-line shift. In the two ``ratio'' rows, the listed
fraction is the sum of
the adverse coefficient ratios and is strictly less than one.
\begin{center}
\tiny
\begin{tabular}{@{}lllll@{}}
\toprule
ID & Variables and domain & Degree & Positive denominator & Exact lower datum \\
\midrule
\(Q_0\) & \(157/50\le x\le10/3,\ 0\le \eta\le1/12000\)
 & \((4,2)\) & \(\mathcal A^2\) & \(6613625187767/70312500000\) \\
\(Q_\infty\) & \(x=10/3+z,\ 0\le \eta\le1/12000\)
 & \((4,2)\) & \(\mathcal A^2\) & ratio \(47333/505500\) \\
\(F_0\) & \(157/50\le x\le10/3,\ 1/23000\le \eta\le1/12000\)
 & \((12,6)\) & \(\mathcal A^6\) & minimum \(>1610047\) \\
\(F_1\) & \(10/3\le x\le5,\ 0\le \eta\le1/22000\)
 & \((12,6)\) & \(\mathcal A^6\) & \(29124973000/19683\) \\
\(F_\infty\) & \(x=5+z,\ \eta=v/3000000,\ 0\leq v\leq1\)
 & \((12,6)\) & \(\mathcal A^6\) & \(432/19073486328125\) \\
\(C_0\) & \(157/50\le x\le10/3,\ 0\le \eta\le1/12000\)
 & \((14,4)\) & \(\mathcal A^4\) & minimum \(>9546672947\) \\
\(C_\infty\) & \(x=10/3+z,\ 0\le \eta\le1/12000\)
 & \((14,4)\) & \(\mathcal A^4\) & ratio \(65989337396066791/77165720550000000\) \\
\bottomrule
\end{tabular}
\end{center}
These seven checks comprise 361 exact rational inequalities.  The derivative
envelopes used below contribute 140 further Bernstein coefficients, of
bidegrees \((j+1,1)\), \(0\le j\le6\); their smallest coefficient is
\(44861/31250\).  Thus the compact domains and the differentiated tail
majorants belong to the same exact certificate.

\subsection{All later modes}

For direct reconstruction of the derivative bounds, put
\(S_j(t)=2^j(-1)^jR_j(t)\). The recurrence gives
\begin{align*}
S_0={}&2t-3,\\
S_1={}&8t^2-30t+15,\\
S_2={}&32t^3-224t^2+330t-75,\\
S_3={}&128t^4-1440t^3+4232t^2-3270t+375,\\
S_4={}&512t^5-8448t^4+41408t^3-68096t^2+30930t-1875,\\
S_5={}&2048t^6-46592t^5+343040t^4-976320t^3
       +1008968t^2-285870t+9375,\\
S_6={}&8192t^7-245760t^6+2536960t^5-11109120t^4
       +20633312t^3-14260064t^2+2610330t-46875.
\end{align*}

For \(t\geq27\), shifting \(t=27+z\) gives positive coefficients in
\((-1)^jR_j(t)\) and in
\(2^{j+1}t^{j+1}-(-1)^jR_j(t)\). Therefore
\begin{equation}\label{eq:R-envelope}
 0<(-1)^jR_j(t)\leq2^{j+1}t^{j+1},
 \qquad 0\leq j\leq6.
\end{equation}
The derivative numerator of the normalized \(n=3\) term is another positive
shifted polynomial, so its absolute value decreases for \(x\geq3\). For
\(n\geq4\), successive majorants have ratio at most
\[
 \left(\frac54\right)^{16}e^{-27}<10^{-9}.
\]
Rational Taylor lower bounds for \(e^{24},e^{27},e^{45}\) then yield, on
\(\pi\leq x\leq5\),
\begin{equation}\label{eq:core-tail}
(|e_0|,\ldots,|e_6|)<
(7\!\cdot\!10^{-9},4\!\cdot\!10^{-7},2\!\cdot\!10^{-4},
7\!\cdot\!10^{-4},3\!\cdot\!10^{-2},1.1,41).
\end{equation}
Indeed, the normalized \(n=3\) term decreases on \(x\geq3\), and
\(e^{24}>25{,}000{,}000{,}000\), so it is bounded by
\(3|R_j(27)|/25{,}000{,}000{,}000\). The sum of the \(n\geq4\) majorants is
at most
\[
 \frac{2^{j+2}3^j4^{2j+4}}{3\cdot10^{19}}.
\]
The data entering these two expressions are
\begin{center}
\small
\begin{tabular}{@{}ccl@{}}
\toprule
\(j\) & \( |R_j(27)| \) & chosen upper bound for \( |e_j| \)\\
\midrule
0 & \(51\) & \(7\cdot10^{-9}\)\\
1 & \(5037/2\) & \(4\cdot10^{-7}\)\\
2 & \(475395/4\) & \(2\cdot10^{-4}\)\\
3 & \(42678141/8\) & \(7\cdot10^{-4}\)\\
4 & \(3623251731/16\) & \(3\cdot10^{-2}\)\\
5 & \(288709329165/32\) & \(11/10\)\\
6 & \(21373315648611/64\) & \(41\)\\
\bottomrule
\end{tabular}
\end{center}
For each row the later-mode expression is less than one thousandth of the
\(n=3\) expression, and their sum is strictly below the chosen bound. This
derives every constant in \eqref{eq:core-tail} from the printed recurrence and
three rational exponential inequalities.
The same Bernstein lemma gives
\[
(|a_0|,\ldots,|a_6|)<(2,5,20,200,2000,60000,1000000).
\]
For any one of the printed raw polynomials
\(N=\sum_\alpha c_\alpha X^\alpha\), the perturbation estimate used here is
the explicit finite sum
\begin{equation}\label{eq:perturbation-formula}
 |N(a+e)-N(a)|
 \leq\sum_\alpha |c_\alpha|
 \left\{\prod_{j=0}^6(A_j+E_j)^{\alpha_j}
              -\prod_{j=0}^6A_j^{\alpha_j}\right\},
\end{equation}
whenever \(|a_j|\leq A_j\) and \(|e_j|\leq E_j\). Substitution of the two
displayed seven-tuples into \eqref{eq:perturbation-formula} gives
\begin{equation}\label{eq:core-perturbation}
 |\Delta N_q|<0.000405,\quad
 |\Delta N_{F_2}|<37.959,\quad
 |\Delta N_{\Cfour}|<31{,}549{,}532.
\end{equation}

For \(x\geq5\), \eqref{eq:R-envelope} gives
\[
 |a_j|\leq2^{j+2}x^j,\qquad
 |e_j|\leq2^{j+2}3^{2j+4}x^je^{-8x}.
\]
The raw weights of \(N_q,N_{F_2},N_{\Cfour}\) are respectively \(2,6,12\).
Thus every perturbation majorant is a positive multiple of
\(x^we^{-8x}\), or a faster-decaying term, with \(w\leq12\); it decreases
for \(x\geq5\). In \eqref{eq:perturbation-formula} take
\[
 A_j=2^{j+2}5^j,\qquad
 E_j=\frac{2^{j+1}3^{2j+4}5^j}{10^{17}}.
\]
The latter follows from the displayed tail bound and
\(\sum_{k=0}^{47}40^k/k!>2\cdot10^{17}\). Direct substitution gives
\begin{equation}\label{eq:outer-perturbation}
 |\Delta N_q|<6.49\cdot10^{-11},\quad
 |\Delta N_{F_2}|<0.03,\quad
 |\Delta N_{\Cfour}|<418{,}287.
\end{equation}
To compare like quantities, note that
\[
 a_0=1+4\eta\frac{R_0(4x)}{R_0(x)}>1,
\]
and, by homogeneity,
\[
 N_{q,1,2}=q_{1,2}a_0^2,\qquad
 N_{F_2,1,2}=(F_2)_{1,2}a_0^6,\qquad
 N_{\Cfour,1,2}=(\Cfour)_{1,2}a_0^4.
\]
Consequently \eqref{eq:two-mode-margin} supplies the same respective lower
margins \(10\), \(1000\), and \(50{,}000{,}000\) for the cleared
numerators.  Both perturbation bounds
\eqref{eq:core-perturbation} and \eqref{eq:outer-perturbation} are strictly
smaller. Their scale relative to the corresponding cleared-numerator margin
is recorded here:
\begin{center}
\small
\begin{tabular}{@{}lcc@{}}
\toprule
target & surviving fraction on \(\pi\leq x\leq5\)
       & surviving fraction on \(x\geq5\)\\
\midrule
\(q\) & \(>0.9999595\) & \(>0.99999999999351\)\\
\(F_2\) & \(>0.962041\) & \(>0.99997\)\\
\(\Cfour\) & \(>0.36900936\) & \(>0.99163426\)\\
\bottomrule
\end{tabular}
\end{center}
Thus even the least relative margin, the compact \(\Cfour\) bound, retains
more than \(36.9\) percent of its certified two-mode numerator margin.
Finally \(\widehat a_0=a_0+e_0>0\), so \eqref{eq:raw-signs} proves all three
signs for \(u\geq0\). Evenness proves Lemma~\ref{lem:certified-input}.
\section{Endpoint algebra for the transport cancellation}\label{app:endpoints}

This appendix records the algebra suppressed by the phrase ``simplifying the
endpoint expression.'' Put
\[
 z=p+L,\qquad w=z+R,\qquad
 a=\frac{Q(z)-Q(p)}L,\qquad b=\frac{Q(w)-Q(z)}R.
\]
Direct integration of \(2-Q''\) gives
\begin{equation}\label{eq:endpoint-delta-Lambda}
 \delta=\frac{L+Q'(p)-a}{L},\qquad
 \Lambda=L+R+a-b.
\end{equation}
Define
\[
 \mathcal J_y=y^3-3yQ(y)+Q(y)Q'(y),
\]
\[
 \mathcal H_p=3p^2-3Q(p)-3pQ'(p)+Q'(p)^2+Q(p)Q''(p),
\]
and, for endpoint data,
\[
 U(c,d)=Q(c)+Q(d)-\frac{Q(d)Q'(d)-Q(c)Q'(c)}{d-c}
 +\frac{(Q(d)-Q(c))^2}{(d-c)^2}.
\]
With \(I_L=\mathcal J_z-\mathcal J_p\) and
\(I_R=\mathcal J_w-\mathcal J_z\), the identity needed in
Lemma~\ref{lem:transport} is exactly
\begin{align*}
&\frac{-(\mathcal J_z-\mathcal J_p)/L
 +(\mathcal J_w-\mathcal J_z)/R}{\Lambda}
 +\frac{L\mathcal H_p-(\mathcal J_z-\mathcal J_p)}{L^2\delta}\\
&\quad=\Lambda+Q'(p)-a
 +\frac{U(p,z)-U(z,w)}{\Lambda}
 +\frac{U(p,z)-Q(p)(2-Q''(p))}{L\delta}.
\end{align*}
To check it, substitute \eqref{eq:endpoint-delta-Lambda}, replace
\(z\) by \(p+L\) and \(w\) by \(p+L+R\), and multiply by the common
denominator \(L^2R\delta\Lambda\). The terms containing \(Q'(w)\), then
\(Q'(z)\), then \(Q''(p)\) cancel pairwise; the remaining endpoint values and
position terms cancel after inserting \(a=(Q(z)-Q(p))/L\) and
\(b=(Q(w)-Q(z))/R\). No differential equation for \(Q\) is used, so the
identity holds for arbitrary smooth \(Q\).
Equivalently, regard the endpoint jets
\(Q(p),Q(z),Q(w),Q'(p),Q'(z),Q'(w),Q''(p)\) and \(p,L,R\) as independent
indeterminates subject only to the displayed definitions of \(a,b,\delta\),
and \(\Lambda\). Clearing \(L^2R\delta\Lambda\) first and then expanding gives
the zero polynomial. Expanding the uncleared rational expression need not
expose this cancellation.
\section{Certificate inventory}\label{app:provenance}

The finite and symbolic parts of the proof are recorded in the following
plain-text source files. Each record states the exact claim, its inputs, and
the corresponding verifier.
\begin{center}
\begin{tabular}{@{}ll@{}}
\toprule
Claim & Proof record \\
\midrule
Global \(q,F_2,\Cfour\), order three &
\texttt{sources/riemann-signs-analytic-certificate.md} \\
Quotient and three-point equivalence &
\texttt{sources/pf4-wronskian-reduction-certificate.md} \\
Transport identity and completion &
\texttt{sources/pf4-transport-kernel-certificate.md} \\
Origin order-five obstruction &
\texttt{sources/pf5-origin-certificate.md} \\
Confluent threshold and finite witness &
\texttt{sources/pf5-threshold-certificate.md} \\
Continuous strict-\(\PF_4\) Fourier separator &
\begin{tabular}[t]{@{}l@{}}
\texttt{sources/continuous-pf4-separator-}\\
\texttt{certificate.md}
\end{tabular} \\
\bottomrule
\end{tabular}
\end{center}
The maintained source map \path{paper/PAPER_MAP.md} identifies the manuscript
section in which each record is used. The single replay command in
\secref{sec:reproducibility} checks the corresponding verifier outputs.
\section{Exact separator calculation}
\label{app:separator}

This appendix records the algebraic boundary behind
\eqref{eq:separator-c4}.  Starting from the cumulants
\(\ell_2,\ldots,\ell_6\), the verifier reconstructs the central moments
\[
 m_0=1,\quad m_1=0,\quad m_2=\ell_2,\quad m_3=\ell_3,
\]
\[
 m_4=\ell_4+3\ell_2^2,\qquad
 m_5=\ell_5+10\ell_3\ell_2,
\]
\[
 m_6=\ell_6+15\ell_4\ell_2+10\ell_3^2+15\ell_2^3,
\]
and then forms \(\det[m_{i+j}]_{i,j=0}^3\) directly.  This independently
regenerates the thirteen-term \(\Cfour\) polynomial; it does not import the
expansion used for the Riemann kernel.

The recurrence \eqref{eq:separator-N-recurrence} is then applied over
\(\mathbb Q[t]\).  Substitution of \eqref{eq:separator-logjets} shows that
each of the thirteen determinant monomials has common denominator \(P^{12}\).
After collecting, the numerator is divisible by \(P^8\) in \(\mathbb Q[t]\).
Cancel this factor and clear the remaining powers of two, writing
\[
 \Cfour[f_*](x)=\frac{\mathcal G(t)}{2^{54}P(t)^4}.
\]
Exact rational arithmetic verifies
\[
 \deg\mathcal G=24,\qquad
 [t^j]\mathcal G=[t^{24-j}]\mathcal G>0
 \quad(0\leq j\leq24),
\]
with smallest integer coefficient
\[
 \min_{0\leq j\leq24}[t^j]\mathcal G=3221225472.
\]
Equivalently, the smallest coefficient before multiplication by \(2^{54}\)
is \(3/2^{24}\). Write
\[
 \mathcal G(t)=\sum_{j=0}^{24}a_jt^j,\qquad a_j=a_{24-j}.
\]
The 13 independent integer coefficients are:
\begin{center}
\tiny
\begin{tabular}{@{}r r@{\qquad}r r@{}}
\toprule
$j$ & $a_j$ & $j$ & $a_j$ \\
\midrule
0 & $3221225472$ & 7 & $357704506872240$ \\
1 & $61435985920$ & 8 & $701640591264080$ \\
2 & $575070935296$ & 9 & $1172880923200640$ \\
3 & $3512452441920$ & 10 & $1684288128586089$ \\
4 & $15702254784944$ & 11 & $2088645133531440$ \\
5 & $54633824917920$ & 12 & $2243243092164284$ \\
6 & $153607464071178$ & & \\
\bottomrule
\end{tabular}
\end{center}
This table is generated by
\path{scripts/generate_separator_coefficients.py}. Its machine-readable
companion \path{generated/separator-coefficients.json} has SHA-256 prefix
\texttt{d0f91259919c7f23}; the complete hash is recorded in the release
manifest.
Coefficient positivity proves the sign on the full domain \(t>0\). Exact spot
reconstructions at \(t=1/3,1,4\) independently compare the
central determinant with \(\mathcal G/(2^{54}P^4)\).

For the Fourier step, the identities
\[
 w+w^{-1}=u,\quad w^2+w^{-2}=u^2-2,\quad
 w^3+w^{-3}=u^3-3u
\]
give \eqref{eq:separator-cubic} directly. Put
\[
 r=e^{1/64},\qquad x=r^2=e^{1/32}.
\]
Exact expansion gives
\[
 \operatorname{disc}(R_c)=4r^{10}G(x),
\]
where
\begin{align*}
G(x)={}&432x^{13}-4968x^9+900x^8+16200x^6+19044x^5\\
&-72600x^4+20000x^3+62100x^2-54334x+13225.
\end{align*}
Writing \(y=x-1\) gives
\begin{align*}
G(1+y)={}&-1-10y-12y^2+680y^3+11532y^4+96660y^5\\
&+365400y^6+569664y^7+512172y^8+303912y^9\\
&+123552y^{10}+33696y^{11}+5616y^{12}+432y^{13}.
\end{align*}
Moreover \(0<y<1/30\). Indeed,
\[
 e<1+1+\frac12+\frac16+\frac1{18}
 =\frac{49}{18}<\frac{11}{4},
\]
where \(1/18=(1/24)\sum_{j\geq0}4^{-j}\) bounds the tail beginning with
\(1/4!\). The binomial theorem gives
\[
 \frac{11}{4}<1+\frac{32}{30}
 +\frac{\binom{32}{2}}{30^2}+\frac{\binom{32}{3}}{30^3}
 =\frac{1891}{675}<\left(\frac{31}{30}\right)^{32}.
\]
The sum of the positive terms at \(y=1/30\) is exactly
\[
 \sum_{j=3}^{13}\frac{[y^j]G(1+y)}{30^j}
 =\frac{1621193195302591}{36905625000000000}<1.
\]
The two omitted terms \(-10y-12y^2\) are negative. Consequently
\[
 G(1+y)<-1+
 \sum_{j=3}^{13}\frac{[y^j]G(1+y)}{30^j}<0,
\]
and hence \(\operatorname{disc}(R_c)<0\) without numerical evaluation.
\section{Direct witness and optional order-five threshold}\label{app:pf5-threshold}

The direct finite witness in \eqref{eq:finite-pf5-witness} is the order-five
input to Theorem~\ref{thm:main}. The remaining cells in this appendix certify
the optional Theorem~\ref{thm:confluent-threshold}. All endpoints lie on
\(10^{-50}\mathbb Z\), and every product and rational scaling is rounded
outward on that lattice. Machin's identity bounds \(\pi\); positive Taylor
sums with a geometric remainder bound \(e^{2u}\); and argument division with
alternating sums bounds the negative exponentials.

The recurrence in the theorem reconstructs \(P_0,\ldots,P_{10}\) over
\(\mathbb Q[x]\). Independently expanding the determinant
\eqref{eq:three-mode-C5} gives a polynomial of degree 23 in \(x\), degree
at most five in each of \(y,z\), and 231 nonzero monomials. On a cell
\(x=a+w\), \(0\leq w\leq d\leq1/10\), the verifier keeps the correlation
between the exponential variables by using
\[
 e^{-rx}=e^{-ra}\sum_{k=0}^8\frac{(-rw)^k}{k!}+E_r(w),
 \qquad
 |E_r(w)|\leq e^{-ra}\frac{(rd)^9}{9!},\qquad r=3,8.
\]
It substitutes these interval polynomials into \(G_3\) and converts the result
to the Bernstein basis in \(w\). The later-mode boxes
\eqref{eq:C5-tail} are propagated through the 120 determinant monomials.

\begin{center}
\small
\begin{tabular}{@{}llll@{}}
\toprule
Object & Domain & Cells & Certified sign \\
\midrule
\(C_5\) & \(0\leq u\leq1/50\) & 2 & negative \\
\(C_5'\) & \(3/200\leq u,\ x\leq4\) & 22 & positive \\
root endpoints & \(u=0.0622795266356,\ 0.0622795266357\) & 2 & \((-,+)\) \\
\(C_5\) & \(4\leq x\leq40\) & 4 & positive \\
one-mode tail & \(x\geq40\) & 1 & positive \\
finite witness & \(u=0,\ h=211/2000\) & 1 & negative \\
\bottomrule
\end{tabular}
\end{center}

At the two root endpoints the fourth theta mode is retained explicitly and
only \(n\geq5\) is bounded. This gives the rational sign margins needed for
the interval of width \(10^{-13}\). For \(x\geq40\), the one-mode determinant
is
\[
 2\cdot150994944\,x^{10}
 (32x^5-240x^4+1200x^3-4200x^2+9450x-10395).
\]
After subtracting \(x^5\), the polynomial has positive coefficients in
\(x-40\). The remaining modes are smaller than this lower bound because
\(x^{10}e^{-3x}\) decreases there; the verifier checks the resulting exact
rational ratio is below one.

The symbolic reconstruction is
\path{scripts/verify_pf5_threshold_symbolic.py}. The independent lattice,
Bernstein, tail, root, and finite-witness replay is
\path{scripts/verify_pf5_threshold.py}.
\end{document}
\typeout{get arXiv to do 4 passes: Label(s) may have changed. Rerun}
