\section{Introduction}\label{sec:introduction}

A function \(f:\R\to\R\) is \(\PF_r\) when every translation-kernel minor
\[
 \det[f(x_i-y_j)]_{i,j=1}^k
\]
is nonnegative for \(1\leq k\leq r\) and increasing node tuples. We call the
property strict when the determinant is positive whenever both tuples are
strictly increasing. This paper determines the exact finite Polya-frequency
order of the Riemann kernel; see \cite{belton} for modern background and
Schoenberg's characterization. Related finite-order and Riemann-kernel work is
placed in \secref{sec:related-work}.

\begin{theorem}[Strict global \(\PF_4\)]\label{thm:main}
For every \(1\leq k\leq4\) and strictly increasing real tuples
\(x_1<\cdots<x_k\) and \(y_1<\cdots<y_k\),
\[
 \det[\Phi(x_i-y_j)]_{i,j=1}^k>0.
\]
\end{theorem}

A parity factorization of the fully confluent derivative matrix at the origin
gives a negative order-five limit. Divided differences then transfer that sign
to equally spaced translation minors at sufficiently small positive spacing;
see Theorem~\ref{thm:not-pf5}. Hence Theorem~\ref{thm:main} has the following
exact consequence.

\begin{corollary}\label{cor:exact-order}
The exact global Polya-frequency order of \(\Phi\) is four.
\end{corollary}

The exact-order classification and the Fourier question are distinct. At the
proved order-four level, the following example shows that finite-order
membership alone does not force Fourier real-rootedness, even within the
positive even Schwartz class.

\begin{theorem}[Continuous \(\PF_4\) Fourier separator]\label{thm:separator}
There is an explicit positive even Schwartz function \(f_*\) which is strict
\(\PF_4\), while its entire Fourier transform has nonreal zeros.
Consequently continuous \(\PF_3\) and continuous \(\PF_4\) membership are
each insufficient to force Fourier real-rootedness.
\end{theorem}

The proof has two certified one-variable inputs and one exact transport
mechanism. First, global inequalities \(q>0\) and \(F_2>0\) imply strict
\(\PF_3\) and positivity of a three-point functional \(\Lambda\). Second, the
fully confluent order-four invariant \(\Cfour\) is globally positive. Exact
quotient identities reduce strict \(\PF_4\) to the monotonicity of a scalar
three-point function \(\Psi\). An increasing curvature coordinate then turns
the derivative of \(\Psi\) into a positive crossing-kernel integral of
\(\Cfour\).

The distinction between a human derivation and a computer certificate is
maintained throughout. Directed interval arithmetic proves the compact and
tail inequalities stated in \secref{sec:inputs}; the structural transport
algebra is written in the paper and independently replayed by repository
verifiers. The exact separator coefficient list is printed in
\appref{app:separator}. The short
order-five certificate uses only exact rational arithmetic and elementary
series bounds. The classification concerns finite-order total positivity
only. It neither proves nor disproves the Riemann Hypothesis.
Theorem~\ref{thm:separator}, proved in \secref{sec:separator}, supplies an
explicit order-four counterexample rather than a finite-order sufficiency
threshold.
