\begin{abstract}
Let \(\Phi\) be the classical Riemann, or de Bruijn--Newman, kernel. We prove
that every translation minor of \(\Phi\) of order at most four is strictly
positive at strictly ordered nodes, and an exact origin-confluent calculation
gives a negative order-five minor. Thus the exact global P\'olya-frequency order
is four. The order-five confluent coefficient changes sign exactly once on the
positive half-line, at
\(0.0622795266356<u_*<0.0622795266357\), and a rational finite-spacing
witness has determinant between \(-1.08\mathbin{\cdot}10^{-7}\) and
\(-1.05\mathbin{\cdot}10^{-7}\). For the positive theorem, a two-mode
argument proves global positivity of the log-curvature quantities \(q,F_2\)
and of the fully confluent invariant \(\Cfour\). The finite verification uses
only rational polynomial algebra, Taylor inequalities, and geometric tails.
The order-five origin, threshold, and finite-witness certificates likewise use
exact rational arithmetic.
A
quotient-Wronskian argument reduces arbitrary fourth-order minors to
\(\partial_\xi\Psi<0\). In the increasing curvature coordinate, its numerator
is
\[
 \delta\Lambda\int_p^w
 \Delta(t)\frac{\Cfour(t)}{Q(t)^6\kappa(t)^2}\dd t.
\]
Here \(\Delta\) is the difference of the CDFs of two explicitly normalized,
curvature-tilted triangular densities. Its strict positivity follows from a
one-crossing density ratio. The transport
reductions and analytic sign estimates are given explicitly, with a table of
the finite polynomial inequalities used for the three global signs.
We then construct an explicit positive even Schwartz kernel which is itself
strictly \(\PF_4\) but whose entire Fourier transform has nonreal zeros; the
latter conclusion follows from a short exact discriminant inequality. This
delimits the finite-order reach of Schoenberg's infinite-order transform
correspondence.
\end{abstract}
