\section{The kernel and smooth even continuation}\label{sec:kernel}

Put
\[
 \vartheta(x)=\sum_{n\in\mathbb Z}e^{-\pi n^2x},\qquad
 \Theta(t)=\vartheta(e^{2t}),\qquad H(t)=e^{t/2}\Theta(t).
\]
This is a real-valued definition: summability is first proved directly for
every \(x>0\), before any analytic continuation is invoked. The real
specialization of Gaussian Poisson summation gives the exact normalization
\(\vartheta(x)=x^{-1/2}\vartheta(1/x)\), and hence
\[
 \Theta(-t)=e^t\Theta(t),\qquad H(-t)=H(t).
\]
A Jacobi-theta realization supplies a globally analytic function agreeing
with this real series. Thus \(H\) is real analytic and even. Define
\[
 \Phi(t)=\frac12\left(H''(t)-\frac14H(t)\right).
\]
This is twice the common de Bruijn kernel normalization; multiplication by a
positive constant changes none of the PF signs or strictness statements.
On \(t\geq0\), locally uniform polynomial--geometric majorants justify
termwise differentiation through order six and give
\begin{equation}\label{eq:kernel-series}
 \Phi(t)=\sum_{n\geq1}
 \left(4\pi^2n^4e^{9t/2}-6\pi n^2e^{5t/2}\right)
 e^{-\pi n^2e^{2t}}.
\end{equation}
Parity reflects this identity to every real \(t\), equivalently by replacing
\(t\) on the right by \(|t|\). Thus the positive-side formula is the
restriction of a real-analytic even function. Smoothness and every derivative
used later at the origin are consequences of that analytic realization, not
of numerical coverage or of differentiating an absolute-value definition.

For \(t\geq0\), the coefficient of the \(n\)-th exponential can be factored as
\[
 2\pi n^2e^{5t/2}\bigl(2\pi n^2e^{2t}-3\bigr)>0,
\]
because \(2\pi>3\). Hence every term in \eqref{eq:kernel-series} is positive
and \(\Phi(t)>0\) on \([0,\infty)\). Evenness gives \(\Phi(t)>0\) on all of
\(\R\), so the following logarithm is globally defined.

Write
\[
 \ell=\log\Phi,\qquad s=\ell',\qquad q=-s'=-\ell''.
\]
For \(a<b\), define
\begin{equation}\label{eq:AM}
 A(a,b)=s(a)-s(b),\qquad
 M(a,b)=\frac{q(b)-q(a)}{A(a,b)}.
\end{equation}
When \(q>0\), \(s\) is strictly decreasing and \(A(a,b)>0\).

\begin{sloppypar}
The maintained formal boundary mirrors this order of construction.
\path{PF4.riemannTheta_modular} is the library-backed Poisson step;
\path{PF4.contDiff_riemannH},
\path{PF4.globalRiemannKernel_even}, and
\path{PF4.globalRiemannKernel_eq_thetaSeries_abs} give analytic continuation,
parity, and the reflected series; and
\path{PF4.GlobalKernelJetIdentification.iteratedDeriv_globalRiemannKernel_eq_thetaSeriesJet}
identifies the complete jet through order six. No project-specific axiom is
used by these declarations.
\end{sloppypar}
