\section{Completion and exact order}\label{sec:completion}

Equation \eqref{eq:sign-bridge} and \eqref{eq:central-identity} imply
\[
 \partial_\xi\Psi(\xi;m,r)<0\qquad(\xi<m<r).
\]
Proposition~\ref{prop:equivalence} therefore proves part~(1) of
Theorem~\ref{thm:main}.

We now prove directly that the classification stops at order four. Let
\(h=211/2000\). Exact rational theta enclosures give
\begin{equation}\label{eq:finite-pf5-witness}
 -1.08\mathbin{\cdot}10^{-7}
 <\det[\Phi((i-j)h)]_{i,j=0}^4
 <-1.05\mathbin{\cdot}10^{-7}.
\end{equation}

\begin{theorem}\label{thm:not-pf5}
The Riemann kernel is not \(\PF_5\).
\end{theorem}

\begin{proof}
The nodes \(0,h,2h,3h,4h\) are strictly increasing. Evenness identifies the
translation matrix with the symmetric Toeplitz matrix determined by the five
kernel values \(\Phi(0),\Phi(h),\ldots,\Phi(4h)\). Each value is enclosed by
exact Taylor bounds for the retained theta modes and the maintained infinite
tail theorem; a rational determinant parity factorization then gives
\eqref{eq:finite-pf5-witness}. This is a negative translation minor at
distinct nodes, with no limiting argument.

\begin{sloppypar}
In the formal development the node ordering, signed-index orientation,
Toeplitz identification, value boxes, determinant sign, and primary-kernel
identity are all premises of
\path{PF4.globalRiemannKernel_orderFive_translationMinor_neg}. Thus the
order-five obstruction used by Theorem~\ref{thm:main} does not depend on the
confluent calculations below.
\end{sloppypar}
\end{proof}

\subsection*{Optional confluent structure}

The origin and threshold calculations give independent information about the
first order-five failure, but are not used in the exact-order assembly. Put
\[
 \mathsf H_k=\det[\Phi^{(i+j)}(0)]_{i,j=0}^{k-1},\qquad
 s_j=\Phi^{(j)}(0).
\]
Since \(\Phi\) is even, simultaneous parity permutations of the rows and
columns give
\[
 \mathsf H_4=AB,\qquad \mathsf H_5=CB,
\]
where
\[
 A=s_0s_4-s_2^2,\qquad B=s_2s_6-s_4^2,
\]
and
\[
 C=\det\begin{pmatrix}
 s_0&s_2&s_4\\
 s_2&s_4&s_6\\
 s_4&s_6&s_8
 \end{pmatrix}.
\]

\begin{lemma}\label{lem:origin-pf5-sign}
For the Riemann kernel,
\[
 445<A<446,\qquad 189223<B<189228,
 \qquad -674000000<C<-614000000.
\]
In particular, \(\mathsf H_4>0\) and \(\mathsf H_5<0\).
\end{lemma}

\begin{proof}
For \(x=\pi n^2e^{2u}\), the \(n\)-th summand of \(\Phi(u)\) is
\(e^{u/2-x}T_0(x)\), where \(T_0(x)=2x(2x-3)\). If its \(j\)-th derivative
is \(e^{u/2-x}T_j(x)\), then
\[
 T_{j+1}=2xT_j'+(1/2-2x)T_j.
\]
Thus
\[
 s_j=\sum_{n\ge1}e^{-\pi n^2}T_j(\pi n^2).
\]
The first three modes are enclosed by rational alternating-series bounds.
Machin's identity
\(\pi=16\arctan(1/5)-4\arctan(1/239)\) supplies rational bounds for \(\pi\),
and argument division followed by the degree-29 and degree-30 alternating
Taylor sums supplies rational bounds for each exponential.

For the omitted modes, let \(S_j\) be the sum of the absolute coefficients of
\(T_j\). Since \(\deg T_j=j+2\), \(3<\pi<22/7\), and
\(e^3>\sum_{r=0}^8 3^r/r!>20\),
\[
 \sum_{n\ge4}|T_j(\pi n^2)|e^{-\pi n^2}
 \leq
 \frac{S_j(22/7)^{j+2}4^{2j+4}20^{-16}}
 {1-(5/4)^{20}20^{-9}}
 \qquad(j=0,2,4,6,8).
\]
All endpoints lie on \(10^{-36}\mathbb Z\), and every arithmetic operation is
rounded outward. Substitution into the displayed formulas gives the entirely
rational sign chain
\[
 0<445<A<446,\qquad 0<189223<B<189228,
\]
\[
 -674000000<C<-614000000<0.
\]
Thus \(AB>0\) and \(CB<0\) without a floating-point determinant. The full
grid endpoints and the standard-library verifier are included in the
reproducibility archive.
\end{proof}

Applying Lemma~\ref{lem:confluent-limit} with \(k=5\), \(z=0\), and
\(a_i=b_i=i\) shows independently that
\(\det[\Phi((i-j)\varepsilon)]_{i,j=0}^4<0\) for every sufficiently small
positive \(\varepsilon\). This implication is not needed for
Theorem~\ref{thm:not-pf5}, whose witness is the fixed rational spacing above.

For the equal-step family put
\[
 D_5(u,h)=\det[\Phi(u+(i-j)h)]_{i,j=0}^4,\qquad
 C_5(u)=\lim_{h\downarrow0}\frac{D_5(u,h)}{h^{20}}.
\]
Because \(V(0,\ldots,4)=\prod_{j=1}^4j!\), the Vandermonde and factorial
factors in Lemma~\ref{lem:confluent-limit} cancel, and therefore
\begin{equation}\label{eq:C5-H5}
 C_5(u)=\det[\Phi^{(i+j)}(u)]_{i,j=0}^4.
\end{equation}

\begin{theorem}[Confluent order-five threshold]\label{thm:confluent-threshold}
There is a unique \(u_*>0\) such that \(C_5(u_*)=0\), and
\[
 0.0622795266356<u_*<0.0622795266357.
\]
Moreover \(C_5(u)<0\) for \(0\leq u<u_*\), while \(C_5(u)>0\) for
\(u>u_*\).
\end{theorem}

\begin{proof}
Put \(x=\pi e^{2u}\), \(y=e^{-3x}\), and \(z=e^{-8x}\). After removing the
positive first-mode amplitude \(2xe^{5u/2-x}\), the first three theta modes of
the derivative jet are
\[
 b_j=P_j(x)+4yP_j(4x)+9zP_j(9x),
\]
where
\[
 P_0(x)=2x-3,\qquad
 P_{j+1}(x)=\left(\frac52-2x\right)P_j(x)+2xP_j'(x).
\]
Thus the three-mode part of \(C_5\), apart from a positive fifth power, is the
closed determinant
\begin{equation}\label{eq:three-mode-C5}
 G_3(x,y,z)=\det[b_{i+j}]_{i,j=0}^4.
\end{equation}
Its exact expansion has 231 monomials. The path derivative is obtained without
another expansion from
\[
 \frac{d}{du}=2x(\partial_x-3y\partial_y-8z\partial_z).
\]

For \(j\leq9\), the omitted modes satisfy
\begin{equation}\label{eq:C5-tail}
 |e_j(x)|\leq
 \frac{S_jx^{j+1}4^{2j+4}e^{-15x}}
 {1-(5/4)^{22}e^{-9x}},
\end{equation}
where \(S_j\) is the sum of the absolute coefficients of \(P_j\). Exact
rational Bernstein bounds, preserving the common \(x\)-dependence of
\(e^{-3x}\) and \(e^{-8x}\), give \(C_5<0\) from \(u=0\) through \(u=1/50\)
and \(C_5'>0\) on the overlapping range from \(u=3/200\) through \(x=4\).
Direct four-mode endpoint enclosures give opposite signs at
\(u=0.0622795266356\) and \(u=0.0622795266357\). Four further Bernstein cells
give \(C_5>0\) for \(4\leq x\leq40\), and the exact one-mode determinant plus
\eqref{eq:C5-tail} gives positivity for \(x\geq40\). These overlapping signs
prove existence, uniqueness, and the stated classification. The domains and
cell counts are listed in \appref{app:pf5-threshold}.
\end{proof}

The outermost center over all finite spacings is a separate two-variable
extremal problem; no such global extremality is used here.

Equation~\eqref{eq:finite-pf5-witness} proves part~(2) of
Theorem~\ref{thm:main}. Together with the strict minors through order four,
this completes the exact-order classification. The preceding confluent
theorem is not used in that assembly.

\begin{remark}[Riemann Hypothesis boundary]
Schoenberg's transform theorem says that the bilateral Laplace transform of a
\(\PF_\infty\) function is the reciprocal of a Laguerre--P\'olya entire function
on its strip of convergence~\cite{schoenberg-ii,belton}. The Fourier transform
of \(\Phi\), up to the standard normalization, is the Riemann \(\Xi\)-function,
which has known real zeros; hence \(\Phi\) is unconditionally not
\(\PF_\infty\). The Schoenberg formulation related to the Riemann Hypothesis
instead asks for the inverse transform of the reciprocal of \(\Xi\) to be a
P\'olya-frequency function~\cite{grochenig}. Thus the finite-order classification
proved here is a different statement. The next section further shows that
strict \(\PF_4\) alone does not imply Fourier real-rootedness.
\end{remark}
