\section{Exact verification and reproduction}\label{sec:reproducibility}

The primary universal theorem is checked by the pinned Lean project in
\path{proof/formal}. From that directory, \texttt{lake build} constructs the
real theta series, analytic kernel and global derivative jet, universal
cleared signs, fixed-order quotient and transport chain, arbitrary-node strict
minors through order four, direct negative order-five witness, and exact-order
assembly. The focused command
\texttt{lake env lean PF4/Audit.lean} prints the axiom dependencies of the
exported declarations. They are exactly \texttt{propext},
\texttt{Classical.choice}, and \texttt{Quot.sound}. No \texttt{sorry},
\texttt{admit}, custom axiom, or unsafe theorem bridge occurs in the target
dependency tree.

The principal claim boundaries are:
\begin{center}
\small
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.25\textwidth}
>{\raggedright\arraybackslash}p{0.66\textwidth}@{}}
\toprule
Object & Maintained boundary \\
\midrule
Analytic kernel and global jet &
\path{PF4.globalRiemannKernel_eq_thetaSeries_abs};
\path{PF4.GlobalKernelJetIdentification.iteratedDeriv_globalRiemannKernel_eq_thetaSeriesJet} \\
Global \(q,F_2,\Cfour\) &
\path{PF4.CERT12OuterClosure.normalized_cleared_signs_pos} and exact raw-jet transfer \\
Lower \(\Lambda\) and orders two--three &
\path{PF4.WeightedMeanVariation.actual_weightedMeanVariation_lowerLambda};
\path{PF4.GlobalStrictPF4.translationMinor_two_pos};
\path{PF4.GlobalStrictPF4.translationMinor_three_pos} \\
Fixed-order quotient cascade &
\path{PF4.FixedOrderQuotientWronskian.fixedOrderFour_quotientWronskian_package} \\
Actual coordinate transport &
\path{PF4.GlobalStrictPF4.globalRiemannKernel_coordinateNumerator_pos};
\path{PF4.GlobalStrictPF4.globalRiemannKernel_coordinatePartialXiPsi_neg} \\
Universal strict PF4 &
\path{PF4.globalRiemannKernel_strictPFUpTo_four} \\
Direct PF5 witness &
\path{PF4.globalRiemannKernel_orderFive_translationMinor_neg} \\
Exact order four &
\path{PF4.globalRiemannKernel_pfOrderExactly_four} \\
\bottomrule
\end{tabular}
\end{center}

Independent exact verifiers reconstruct the printed finite algebra and
rational inequalities:
\begin{center}
\small
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.30\textwidth}
>{\raggedright\arraybackslash}p{0.51\textwidth}
>{\raggedright\arraybackslash}p{0.12\textwidth}@{}}
\toprule
Object & Repository replay & Role \\
\midrule
Global \(q,F_2,\Cfour\) &
\path{scripts/verify_riemann_signs_exact.py} & exact arithmetic \\
Fixed Wronskian algebra &
\path{scripts/verify_pf4_wronskian_reduction.py} & independent \\
Endpoint transport algebra &
\path{scripts/verify_pf4_transport_kernel.py} & independent \\
Direct PF5 witness and optional threshold &
\path{scripts/verify_pf5_threshold.py} & exact arithmetic \\
Optional threshold polynomial &
\path{scripts/verify_pf5_threshold_symbolic.py} & independent \\
Continuous separator &
\path{scripts/verify_continuous_pf4_separator.py} & exact arithmetic \\
\bottomrule
\end{tabular}
\end{center}

The global-sign replay retains the first two theta modes exactly. It checks
the 361 Bernstein and decay inequalities summarized in \appref{app:tail}, the
140 derivative-envelope coefficients, and analytic geometric bounds for every
mode \(n\geq3\). It uses a pure-Python rational domain and refuses a FLINT
import. No floating-point comparison or interval subdivision decides a sign.

The PF5 replay directly encloses the five kernel values at spacings
\(0,h,2h,3h,4h\), \(h=211/2000\), and proves the determinant interval
\eqref{eq:finite-pf5-witness}. Its additional cells reconstruct the optional
231-monomial confluent determinant and unique threshold. The separator replay
checks the exact \(P^8\) cancellation, all 25 coefficients in
\eqref{eq:separator-c4}, and the rational discriminant inequality in
\appref{app:separator}.

From the repository root, the independent artifact command is
\begin{center}
\texttt{python scripts/replay\_paper.py}.
\end{center}
It prints one \texttt{PASS} line per active exact certificate followed by
\texttt{status=paper evidence replay passed}. Package versions, the complete
stdout digest, PDF digest, and arXiv archive digest are recorded in
\path{paper/RELEASE_MANIFEST.md}. Earlier computer-algebra experiments are
discovery provenance only; the maintained Lean declarations and exact replay
boundaries above carry the final claims.
