\section{Declarations, availability, and computational provenance}

\paragraph{Author contribution.}
Joshuah Rainstar conceived and directed the project, developed the proof
architecture, verified the exact computations, and prepared
the manuscript.

\paragraph{Acknowledgments and computational assistance.}
The author acknowledges the use of OpenAI Codex and ChatGPT, Anthropic Claude,
and Moonshot AI Kimi for symbolic calculation, implementation, drafting, and
review. The author takes responsibility for the mathematical claims and the
final manuscript.

\paragraph{Conflict of interest.}
The author declares no competing interests.

\paragraph{Code and data availability.}

The public repository is
\url{https://github.com/falseywinchnet/zeta}. The submitted manuscript is
preserved by the immutable tag \texttt{pf4-paper-v1.0.0}. Its commit is
\begin{center}
\texttt{4a14988093d7afaf05f453f8daf5441c09ba58b3}.
\end{center}
The present revised proof is release \texttt{PF4-paper-v2.0.0}, recorded by
MIND epoch \texttt{P000163}.
Their distinct status and material proof changes are listed in
\path{paper/REVISION_HISTORY.md}; current source, environment, replay, PDF, and
archive digests are listed in \path{paper/RELEASE_MANIFEST.md}. The repository
archive is assigned DOI \url{https://doi.org/10.5281/zenodo.21404360}.

The formal replay is \texttt{lake build} followed by
\texttt{lake env lean PF4/Audit.lean} from \path{proof/formal}. The independent
exact arithmetic replay is \texttt{python scripts/replay\_paper.py} from the
repository root.

All theorem-bearing sign decisions are exact. Numerical values produced by
the repository scripts are diagnostic only; there is no separate experimental
dataset.
